---
title: "Chapter 2 - Bite Data - chemmistry - Predicted chemmistry at Cedar Gulch"
output:
  pdf_document: default
  html_document: default
---

This R Markdown file will input data for the Cedar Gulch (JN Gulch = Leadore = Lemhi = Cedar Gulch) site and prepare it for three downstream analyses determining the effects of chemistry and predicted chemistry on bite data. 

Cedar Gulch is a pygmy rabbit site that underwent stratified random collection of data, with 3-6 plants sampled per patch and patches randomly selected within distance strata for dist to burrow (0-20m; 20-40m; 40-100m). While data points include a combination of individual plants and pooled samples, only the individual plant samples were used. Data was collected in Summer and Winter, and had no upper limit for the number of bites counted. A negative binomial distribution was used to analyze this data set.

In addition to these data, individual pellet counts within a meter of each individual shrub.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#Load libraries
library("rprojroot")
library("loo")
library("rstanarm")
options(mc.cores = parallel::detectCores())
library("ggplot2")
library("bayesplot")
theme_set(bayesplot::theme_default(base_family = "sans"))
library("MASS")
library("lme4")
library("brms")
library("rstanarm")
```

# Functions

These functions are used throughout the markdown, and include ways for evaluating predictive error and standardizing the inputs. 

## Root mean square error (RSME)
This shows the difference between an estimator and the values observed, and provides a measure of accuracy.

## Mean absolute error (MAE)
This is a measure of errors between paired observations expressing the same phenomenon, and is one of a number of ways of comparing forecasts with their eventual outcomes.

## Residual sum of squares (RSS)
This is a measure of discrepancy between the data (x) and the model (d). A small value indicates a good fit between the data and the model (0 is a perfect fit). This number can be infinite, as far as I'm aware.

## Total sum of squares (TSS)

This is the explained sum of squares plus the RSS. 

## R2

The proportion of variance explained by the model out of the total variance in the data (0-1). Closer to one means 100% fit. 

## splt

Tidies up the data by removing the double names

## stdize

Putting all of the covariates on the same scale 
http://www.stat.columbia.edu/~gelman/research/published/standardizing7.pdf


```{r}
# This first function is for root mean square, where m is the model predictions, and x is the data.
rmse <- function(m,x) 
{
  sqrt(mean((x-m)^2,na.rm=T))
}

# This function is for mean absolute error, where m is the model predictions, and x is the data. 
mae <- function(m,x)
{
  mean(abs(((x-m))),na.rm=T)
}

# This function is for residual sum of squares
RSS <- function(m,x) 
{
  sum((((m))-(x))^2)
}

# This function is for total sum of squares
TSS <- function(x) 
{
  sum(((x)-(mean(x)))^2)
  }

R2<-function(m,x,logo=F) {
  mors<-na.omit(data.frame(m,x))
  m<-mors$m
  x<-mors$x
  
  if(logo==F) {return(1-RSS(m,x)/TSS(x))} else {return(1-RSS1(m,x)/TSS1(x))}
}

# Split names
splt=function(x,split,num) {
  
  x<-as.character(x)
  p1=strsplit(x,split=split,fixed=T)
  p2=unlist(lapply(p1,"[",num))
  return(p2)
}

# Standardize covariates
stdize<-function(x) {(x-mean(x,na.rm=T))/(2*sd(x,na.rm=T))}

```

# Read in Files

Time to read in all those bite files! 

In Brecken's bite file (BB) for the Cedar Gulch site, you'll see that the number of bites are taken from individual plants, but the data for compilation (e.g., pooled) sites exists. Here, we are only taking information from individual plants. 

```{r}
#Main data set that includes all the sites, chemotype levels. We're setting periods and blank spaces to read in to R as NA:

BB <- read.csv("All_Datasheets.csv", na.strings=c("."," ","","NA"))
BB <- unique(BB)

# Subset to just the KG Magic site. 
Cedar<-subset(BB,BB$Site=="Cedar Gulch")

## Check out the dimensions of the input data:
# Bites
length(Cedar$Bites)
table(Cedar$Bites)

# Season
table(Cedar$Season)

# Species
table(Cedar$Species)

# Plant height
table(Cedar$PlantSize)
# Not available at this site

# Patch type
table(Cedar$PatchType)

#Patch_ID here is the random effect

table(Cedar$Patch_ID)[-which(table(Cedar$Patch_ID)==0)]

# Standardize our covariates

Cedar$CP_Pred_std<-stdize(Cedar$CP_Pred)
Cedar$Phenolics_Pred_std<-stdize(Cedar$Phenolics_Pred)
Cedar$Monoterpenes_Pred_std<-stdize(Cedar$Monoterpenes_Pred)

Cedar$CP_Ref_std<-stdize(Cedar$CP_Ref)
Cedar$Phenolics_Ref_std<-stdize(Cedar$Phenolics_Ref)
Cedar$Monoterpenes_Ref_std<-stdize(Cedar$Monoterpenes_Ref)

Cedar$Patch_ID<-droplevels(as.factor(paste("p",Cedar$Patch_ID.x,sep="_")))

# Create the data set that we use moving forward
Cedar_use<-na.omit(data.frame(Bites=Cedar$Bites,CP_Pred_std=Cedar$CP_Pred_std,PatchType=Cedar$PatchType,Season=Cedar$Season,Phenolics_Pred_std=Cedar$Phenolics_Pred_std,Monoterpenes_Pred_std=Cedar$Monoterpenes_Pred_std,Patch_ID=Cedar$Final_patch,CP_Ref_std=Cedar$CP_Ref_std,Phenolics_Ref_std=Cedar$Phenolics_Ref_std,Monoterpenes_Ref_std=Cedar$Monoterpenes_Ref_std))

#If bites >0, then 1. If not, 0 (creating a binomial distribution)
Cedar_use$Bites_Binomial <- ifelse(Cedar_use$Bites > 0, 1, 0)

## Check out the dimensions of the final data:
# Bites
length(Cedar_use$Bites_Binomial)
table(Cedar_use$Bites_Binomial)

# Season
table(Cedar_use$Season)

# Patch type
table(Cedar_use$PatchType)

min(Cedar_use$CP_Ref_std)
max(Cedar_use$CP_Ref_std) 

min(Cedar_use$CP_Pred_std)
max(Cedar_use$CP_Pred_std)

min(Cedar_use$Phenolics_Ref_std)
max(Cedar_use$Phenolics_Ref_std)

min(Cedar_use$Phenolics_Pred_std)
max(Cedar_use$Phenolics_Pred_std)

min(Cedar_use$Monoterpenes_Ref_std)
max(Cedar_use$Monoterpenes_Ref_std)

min(Cedar_use$Monoterpenes_Pred_std)
max(Cedar_use$Monoterpenes_Pred_std)

## Descriptive Stats

# Crude Proteins

mean(Cedar$CP_Ref, na.rm=TRUE) 
sd(Cedar$CP_Ref, na.rm=TRUE) 

mean(Cedar$CP_Pred, na.rm=TRUE) 
sd(Cedar$CP_Pred, na.rm=TRUE)

mean(Cedar_use$CP_Ref_std, na.rm=TRUE)
sd(Cedar_use$CP_Ref_std, na.rm=TRUE)

mean(Cedar_use$CP_Pred_std, na.rm=TRUE) 
sd(Cedar_use$CP_Pred_std, na.rm=TRUE)

# Monoterpenes
mean(Cedar$Monoterpenes_Ref, na.rm=TRUE) 
sd(Cedar$Monoterpenes_Ref, na.rm=TRUE)

mean(Cedar$Monoterpenes_Pred, na.rm=TRUE)
sd(Cedar$Monoterpenes_Pred, na.rm=TRUE)

mean(Cedar_use$Monoterpenes_Ref_std, na.rm=TRUE)
sd(Cedar_use$Monoterpenes_Ref_std, na.rm=TRUE)

mean(Cedar_use$Monoterpenes_Pred_std, na.rm=TRUE)
sd(Cedar_use$Monoterpenes_Pred_std, na.rm=TRUE)

# Phenolics
mean(Cedar$Phenolics_Ref, na.rm=TRUE)
sd(Cedar$Phenolics_Ref, na.rm=TRUE)

mean(Cedar$Phenolics_Pred, na.rm=TRUE)
sd(Cedar$Phenolics_Pred, na.rm=TRUE)

mean(Cedar_use$Phenolics_Ref_std, na.rm=TRUE)
sd(Cedar_use$Phenolics_Ref_std, na.rm=TRUE)

mean(Cedar_use$Phenolics_Pred_std, na.rm=TRUE)
sd(Cedar_use$Phenolics_Pred_std, na.rm=TRUE)

```

# Question 1: what are the effects of chemmistry on bites?

```{r}

mREF_Cedar_single <-rstanarm::stan_glmer(Bites_Binomial~Season+CP_Ref_std+Phenolics_Ref_std+Monoterpenes_Ref_std+(1|Patch_ID),data=Cedar_use,cores=4, family = "binomial",iter=10000)

png(file="./Cedar_Gulch_Reference.png")
summary(mREF_Cedar_single)
plot(mREF_Cedar_single,regex_pars="_std")

save(mREF_Cedar_single, file = "mREF_Cedar_single.Rdata")

##############
# Extract posteriors

Cedar_single_REF <- as.data.frame(mREF_Cedar_single)

Phenolics_out <- Cedar_single_REF$Phenolics_Ref_std
Phenolics_REF_cat <- rep("Phenolics_REF",times=length(Phenolics_out))

CP_out <- Cedar_single_REF$CP_Ref_std
CP_REF_cat <- rep("CP_REF",times=length(CP_out))

Monoterpenes_out <- Cedar_single_REF$Monoterpenes_Ref_std
Monoterpenes_REF_cat <- rep("Monoterpenes_REF",times=length(Monoterpenes_out))

pos_draws <- c(Phenolics_out,CP_out,Monoterpenes_out)

chemm_type <- c(Phenolics_REF_cat,CP_REF_cat,Monoterpenes_REF_cat)

Cedar_single_REF <- data.frame(pos_draws,chemm_type)

Cedar_single_REF$Site<-rep("Cedar",times=nrow(Cedar_single_REF))

save(Cedar_single_REF ,file="Cedar_single_REF.Rdata")

```

# Question 2: does inference on chemmistry effects change when using predicted, rather than observed values?

```{r}

mPRED_Cedar_single <-rstanarm::stan_glmer(Bites_Binomial~Season+CP_Pred_std+Phenolics_Pred_std+Monoterpenes_Pred_std+(1|Patch_ID),data=Cedar_use,cores=4, family = "binomial",iter=10000)

png(file="./Cedar_Pred.png")
summary(mPRED_Cedar_single)
plot(mPRED_Cedar_single,regex_pars="_std")
dev.off()

save(mPRED_Cedar_single, file = "mPRED_Cedar_single.Rdata")

##############
# Extract posteriors

Cedar_single_PRED <- as.data.frame(mPRED_Cedar_single)

Phenolics_out <- Cedar_single_PRED$Phenolics_Pred_std
Phenolics_PRED_cat <- rep("Phenolics_PRED",times=length(Phenolics_out))

CP_out <- Cedar_single_PRED$CP_Pred_std
CP_PRED_cat <- rep("CP_PRED",times=length(CP_out))

Monoterpenes_out <- Cedar_single_PRED$Monoterpenes_Pred_std
Monoterpenes_PRED_cat <- rep("Monoterpenes_PRED",times=length(Monoterpenes_out))

pos_draws <- c(Phenolics_out,CP_out,Monoterpenes_out)

chemm_type <- c(Phenolics_PRED_cat,CP_PRED_cat,Monoterpenes_PRED_cat)

Cedar_single_PRED <- data.frame(pos_draws,chemm_type)

Cedar_single_PRED$Site<-rep("Cedar",times=nrow(Cedar_single_PRED))

save(Cedar_single_PRED ,file="Cedar_single_PRED.Rdata")

```

# Question 3: how does the predictions changes when using obs vs predicted chemmistry?

# https://onlinelibrary.wiley.com/doi/full/10.1111/ecog.02881
#paper that describes our leave-one-out approach

```{r}

# In this code, we are creating subsets of the data
Cedar_levs<-unique(Cedar_use$Patch_ID)
Cedar_in<-vector("list",length(Cedar_levs))
Cedar_out<-vector("list",length(Cedar_levs))

# We are testing three different models:
# Model 1 is the observed chemmistry
# Model 2 is the predicted chemmistry
# Model 3 is a null model with no chemmistry
ref_preds<-vector("list",length(Cedar_levs))
pred_preds<-vector("list",length(Cedar_levs))
null_preds<-vector("list",length(Cedar_levs))

for(i in 1:length(Cedar_levs)) #Cedar_levs is the unique number of patch ids
{
  # For each one of if (!requireNamespace("devtools", quietly = TRUE)){install.packages("devtools")} devtools::install_github("jbisanz/qiime2R")the patch ids, this is looping through. If you want to trouble shoot this, put i = 1 into the r consul and run line by line. Patch id out, running the model, and predicting on the left out patch
  
  # Data use to fit the model
  Cedar_in[[i]]<-Cedar_use[-which(Cedar_use$Patch_ID==Cedar_levs[i]),]
  
  # Data used to test the model
  Cedar_out[[i]]<-Cedar_use[which(Cedar_use$Patch_ID==Cedar_levs[i]),]
  
  m0_Cedar<-stan_glmer(Bites_Binomial~Season+(1|Patch_ID),data=Cedar_in[[i]],cores=4, family = "binomial",iter=10000)
  
  # Making predictions for the left out data
  null_preds[[i]]=posterior_epred(m0_Cedar,newdata=Cedar_out[[i]])
  
  mPRED_Cedar<-stan_glmer(Bites_Binomial~Season+CP_Pred_std+Phenolics_Pred_std+Monoterpenes_Pred_std+(1|Patch_ID),data=Cedar_in[[i]],cores=4, family = "binomial",iter=10000)
  
  pred_preds[[i]]=posterior_epred(mPRED_Cedar,newdata=Cedar_out[[i]])
  
  mREF_Cedar<-stan_glmer(Bites_Binomial~Season+CP_Ref_std+Phenolics_Ref_std+Monoterpenes_Ref_std+(1|Patch_ID),data=Cedar_in[[i]],cores=4, family = "binomial",iter=10000)
  
  ref_preds[[i]]<-posterior_epred(mREF_Cedar,newdata=Cedar_out[[i]])
  }

null_preds_t<-t(null_preds)

# Extracting the predictions
# Binding the results together in a single data frame
Cedar_logo<-vector("list",4)
names(Cedar_logo)<-c("out_data","null","ref","pred")
Cedar_logo[[1]]<-do.call("rbind",Cedar_out)
Cedar_logo[[2]]<-t(do.call("cbind",null_preds))
Cedar_logo[[3]]<-t(do.call("cbind",ref_preds))
Cedar_logo[[4]]<-t(do.call("cbind",pred_preds))

# Save the object 
save(Cedar_logo,file="Cedar_logo.Rdata")

# Load(file="Cedar_logo.Rdata")
str(Cedar_logo)

# Predicted data
# These are the predictions from the three models above. These are matrices, because we are doing this in a Bayesian context. 
null_preds=Cedar_logo$null

ref_preds=Cedar_logo$ref

pred_preds=Cedar_logo$pred

# New variable
Cedar_obs<-Cedar_logo$out_data$Bites

# New variable (not sure what this would be in KG_Magic)
Cedar_total <- Cedar_logo$out_data$Bites

# 1 = whether you're doing the mean across rows or columns
# Trying to predict across patchm, to create something in a list. 
Cedar_null<-apply(null_preds,1,mean)
length(Cedar_null)
Cedar_ref<-apply(ref_preds,1,mean)
length(Cedar_ref)
Cedar_pred<-apply(pred_preds,1,mean)
length(Cedar_pred)

# Mean absolute error, defined above. This is on the scale of the data, so the negative log likelihoods (which are a bit abstract) make more sense. 
mae(Cedar_null,Cedar_obs) 
mae(Cedar_ref,Cedar_obs)
mae(Cedar_pred, Cedar_obs)

```

# General posterior draw descriptive statistics

```{r}

nameo <- list.files()[-1]

chemm_range <- read.csv("Text_Chemistry_Mins_Max_13July2023.csv")

load("mREF_Cedar_single.Rdata")
load("mPRED_Cedar_single.Rdata")

#All chemicals
chemm <- read.csv("Text_Chemistry_Mins_Max_13July2023.csv")

#First we will pull out the posterior draws:
ref_cedar_posteriors <- data.frame(mREF_Cedar_single)
pred_cedar_posteriors <- data.frame(mPRED_Cedar_single)

dim(ref_cedar_posteriors)
dim(pred_cedar_posteriors)

```

# Probability of Direction - Reference chemmistry

What is the percentage of draws that are either positive of negative?

```{r}

# Crude Proteins
length(which(ref_cedar_posteriors$CP_Ref_std>0))/length(ref_cedar_posteriors$CP_Ref_std)
length(which(ref_cedar_posteriors$CP_Ref_std<0))/length(ref_cedar_posteriors$CP_Ref_std)

# Monoterpenes
length(which(ref_cedar_posteriors$Monoterpenes_Ref_std>0))/length(ref_cedar_posteriors$Monoterpenes_Ref_std)
length(which(ref_cedar_posteriors$Monoterpenes_Ref_std<0))/length(ref_cedar_posteriors$Monoterpenes_Ref_std)

# Phenolics
length(which(ref_cedar_posteriors$Phenolics_Ref_std>0))/length(ref_cedar_posteriors$Phenolics_Ref_std)
length(which(ref_cedar_posteriors$Phenolics_Ref_std<0))/length(ref_cedar_posteriors$Phenolics_Ref_std)

```

# Probability of Direction - Predicted chemmistry

What is the percentage of draws that are either positive of negative?

```{r}
# Crude Proteins
length(which(pred_cedar_posteriors$CP_Pred_std>0))/length(pred_cedar_posteriors$CP_Pred_std)
length(which(pred_cedar_posteriors$CP_Pred_std<0))/length(pred_cedar_posteriors$CP_Pred_std)

# Monoterpenes
length(which(pred_cedar_posteriors$Monoterpenes_Pred_std>0))/length(pred_cedar_posteriors$Monoterpenes_Pred_std)
length(which(pred_cedar_posteriors$Monoterpenes_Pred_std<0))/length(pred_cedar_posteriors$Monoterpenes_Pred_std)

# Phenolics
length(which(pred_cedar_posteriors$Phenolics_Pred_std>0))/length(pred_cedar_posteriors$Phenolics_Pred_std)
length(which(pred_cedar_posteriors$Phenolics_Pred_std<0))/length(pred_cedar_posteriors$Phenolics_Pred_std)

```

# Effect Size Min & Max - Reference chemmistry

```{r}

# Referencing min and max from data frame
chemm$Ref_Min[which(chemm$Site=="Cedar" & chemm$Chemical=="Crude Protein")] 
chemm$Ref_Max[which(chemm$Site=="Cedar" & chemm$Chemical=="Crude Protein")] 

# Setting up an empty vector to fill in with predictions
predicted_diff_cp_ref <- rep(NA,times=ncol(ref_cedar_posteriors))
predicted_diff_Monoterpenes_ref <- rep(NA,times=ncol(ref_cedar_posteriors))
predicted_diff_Phenolics_ref <- rep(NA,times=ncol(ref_cedar_posteriors))

# CP
for(i in 1:ncol(ref_cedar_posteriors)){

# This is just an intercept + slope*x. plogis ensures it is a probability. We are looping over every value of the posterior draw to propagate uncertainty.
min_pred<-plogis(ref_cedar_posteriors$X.Intercept.[i]+ref_cedar_posteriors$CP_Ref_std[i]*chemm$Ref_Min[which(chemm$Site=="Cedar" & chemm$Chemical=="Crude Protein")])
  
max_pred<-plogis(ref_cedar_posteriors$X.Intercept.[i]+ref_cedar_posteriors$CP_Ref_std[i]*chemm$Ref_Max[which(chemm$Site=="Cedar" & chemm$Chemical=="Crude Protein")])
  
predicted_diff_cp_ref[i]<-max_pred-min_pred # This is the difference we will store. 
  }  

quantile(predicted_diff_cp_ref,c(0.025,0.5,0.975)) 

# Monoterpenes
for(i in 1:ncol(ref_cedar_posteriors)){

# This is just an intercept + slope*x. plogis ensures it is a probability. We are looping over every value of the posterior draw to propagate uncertainty.
min_pred<-plogis(ref_cedar_posteriors$X.Intercept.[i]+ref_cedar_posteriors$Monoterpenes_Ref_std[i]*chemm$Ref_Min[which(chemm$Site=="Cedar" & chemm$Chemical=="Monoterpenes")])
  
max_pred<-plogis(ref_cedar_posteriors$X.Intercept.[i]+ref_cedar_posteriors$Monoterpenes_Ref_std[i]*chemm$Ref_Max[which(chemm$Site=="Cedar" & chemm$Chemical=="Monoterpenes")])
  
predicted_diff_Monoterpenes_ref[i]<-max_pred-min_pred # This is the difference we will store. 
}  

quantile(predicted_diff_Monoterpenes_ref,c(0.025,0.5,0.975)) 

# Phenolics
for(i in 1:ncol(ref_cedar_posteriors)){

# This is just an intercept + slope*x. plogis ensures it is a probability. We are looping over every value of the posterior draw to propagate uncertainty.
min_pred<-plogis(ref_cedar_posteriors$X.Intercept.[i]+ref_cedar_posteriors$Phenolics_Ref_std[i]*chemm$Ref_Min[which(chemm$Site=="Cedar" & chemm$Chemical=="Phenolics")])
  
max_pred<-plogis(ref_cedar_posteriors$X.Intercept.[i]+ref_cedar_posteriors$Phenolics_Ref_std[i]*chemm$Ref_Max[which(chemm$Site=="Cedar" & chemm$Chemical=="Phenolics")])
  
predicted_diff_Phenolics_ref[i]<-max_pred-min_pred # This is the difference we will store. 
}  

quantile(predicted_diff_Phenolics_ref,c(0.025,0.5,0.975)) 

```

# Effect Size Min & Max - Predicted chemmistry

```{r}

# Referencing min and max from data frame
chemm$Pred_Min[which(chemm$Site=="Cedar" & chemm$Chemical=="Crude Protein")] 
chemm$Pred_Max[which(chemm$Site=="Cedar" & chemm$Chemical=="Crude Protein")] 

# Setting up an empty vector to fill in with predictions
predicted_diff_cp_pred <- rep(NA,times=ncol(pred_cedar_posteriors))
predicted_diff_Monoterpenes_pred <- rep(NA,times=ncol(pred_cedar_posteriors))
predicted_diff_Phenolics_pred <- rep(NA,times=ncol(pred_cedar_posteriors))

# CP
for(i in 1:ncol(pred_cedar_posteriors)){

# This is just an intercept + slope*x. plogis ensures it is a probability. We are looping over every value of the posterior draw to propagate uncertainty.
min_pred<-plogis(pred_cedar_posteriors$X.Intercept.[i]+pred_cedar_posteriors$CP_Pred_std[i]*chemm$Pred_Min[which(chemm$Site=="Cedar" & chemm$Chemical=="Crude Protein")])
  
max_pred<-plogis(pred_cedar_posteriors$X.Intercept.[i]+pred_cedar_posteriors$CP_Pred_std[i]*chemm$Pred_Max[which(chemm$Site=="Cedar" & chemm$Chemical=="Crude Protein")])
  
predicted_diff_cp_pred[i]<-max_pred-min_pred # This is the difference we will store. 
  }  

quantile(predicted_diff_cp_pred,c(0.025,0.5,0.975)) 

# Monoterpenes
for(i in 1:ncol(pred_cedar_posteriors)){

# This is just an intercept + slope*x. plogis ensures it is a probability. We are looping over every value of the posterior draw to propagate uncertainty.
min_pred<-plogis(pred_cedar_posteriors$X.Intercept.[i]+pred_cedar_posteriors$Monoterpenes_Pred_std[i]*chemm$Pred_Min[which(chemm$Site=="Cedar" & chemm$Chemical=="Monoterpenes")])
  
max_pred<-plogis(pred_cedar_posteriors$X.Intercept.[i]+pred_cedar_posteriors$Monoterpenes_Pred_std[i]*chemm$Pred_Max[which(chemm$Site=="Cedar" & chemm$Chemical=="Monoterpenes")])
  
predicted_diff_Monoterpenes_pred[i]<-max_pred-min_pred # This is the difference we will store. 
}  

quantile(predicted_diff_Monoterpenes_pred,c(0.025,0.5,0.975)) 

# Phenolics
for(i in 1:ncol(pred_cedar_posteriors)){

# This is just an intercept + slope*x. plogis ensures it is a probability. We are looping over every value of the posterior draw to propagate uncertainty.
min_pred<-plogis(pred_cedar_posteriors$X.Intercept.[i]+pred_cedar_posteriors$Phenolics_Pred_std[i]*chemm$Pred_Min[which(chemm$Site=="Cedar" & chemm$Chemical=="Phenolics")])
  
max_pred<-plogis(pred_cedar_posteriors$X.Intercept.[i]+pred_cedar_posteriors$Phenolics_Pred_std[i]*chemm$Pred_Max[which(chemm$Site=="Cedar" & chemm$Chemical=="Phenolics")])
  
predicted_diff_Phenolics_pred[i]<-max_pred-min_pred # This is the difference we will store. 
}  

quantile(predicted_diff_Phenolics_pred,c(0.025,0.5,0.975)) 

```
