---
title: "Chapter 2 - Bite Data - Chemistry - Predicted Chemistry at Craters Site"
output:
  pdf_document: default
  html_document: default
---

This R Markdown file will input data for the Craters site and prepare it for three downstream analyses determining the effects of chemistry and predicted chemistry on bite data.

Craters is a Greater Sage-grouse site that sampled using a stratified random (within patch boundary) using 3 plants for each morphotype (size + species) for browsed and unbrowsed plants at each patch pooled into each sample. All samples were pooled for chemistry per morphotype, but bite mark data exists for individual plants through Marcella's data. Data was collected in Winter only. There is an upper limit of 50 bites for some of these individuals, so proportional data was used with an upper limit of 50. A binomial distribution was used to analyze this data set.

# Input libraries

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#Load libraries
library("rprojroot")
library("loo")
library("rstanarm")
options(mc.cores = parallel::detectCores())
library("ggplot2")
library("bayesplot")
theme_set(bayesplot::theme_default(base_family = "sans"))
library("MASS")
library("lme4")
library("brms")

```

# Functions

These functions are used throughout the markdown, and include ways for evaluating predictive error and standardizing the inputs. 

## Root mean square error (RSME)
This shows the difference between an estimator and the values observed, and provides a measure of accuracy.

## Mean absolute error (MAE)
This is a measure of errors between paired observations expressing the same phenomenon, and is one of a number of ways of comparing forecasts with their eventual outcomes.

## Residual sum of squares (RSS)
This is a measure of discrepancy between the data (x) and the model (d). A small value indicates a good fit between the data and the model (0 is a perfect fit). This number can be infinite, as far as I'm aware.

## Total sum of squares (TSS)

This is the explained sum of squares plus the RSS. 

## R2

The proportion of variance explained by the model out of the total variance in the data (0-1). Closer to one means 100% fit. 

## splt

Tidies up the data by removing the double names

## stdize

Putting all of the covariates on the same scale 
http://www.stat.columbia.edu/~gelman/research/published/standardizing7.pdf

```{r}
# This first function is for root mean square, where m is the model predictions, and x is the data.
rmse <- function(m,x) 
{
  sqrt(mean((x-m)^2,na.rm=T))
}

# This function is for mean absolute error, where m is the model predictions, and x is the data. 
mae <- function(m,x)
{
  mean(abs(((x-m))),na.rm=T)
}

# This function is for residual sum of squares
RSS <- function(m,x) 
{
  sum((((m))-(x))^2)
}

# This function is for total sum of squares
TSS <- function(x) 
{
  sum(((x)-(mean(x)))^2)
  }

R2<-function(m,x,logo=F) {
  mors<-na.omit(data.frame(m,x))
  m<-mors$m
  x<-mors$x
  
  if(logo==F) {return(1-RSS(m,x)/TSS(x))} else {return(1-RSS1(m,x)/TSS1(x))}
}

# Split names
splt=function(x,split,num) {
  
  x<-as.character(x)
  p1=strsplit(x,split=split,fixed=T)
  p2=unlist(lapply(p1,"[",num))
  return(p2)
}

# Standardize covariates
stdize<-function(x) {(x-mean(x,na.rm=T))/(2*sd(x,na.rm=T))}
```

# Read in Files

Note, we are using a binomial distribution for bite data here. This will have to be done with pooled samples. 

```{r}
# Main data set that includes all the sites, chemotype levels. We're setting periods and blank spaces to read in to R as NA:
BB <- read.csv("All_Datasheets.csv", na.strings=c("."," ","","NA"))
BB <- unique(BB)

# Individual plants, contains bite data from individual plants
mbites<-read.csv("marcella_bites.csv",na.strings=c("."," ","","NA"))

# Define the number of trials for the binomial distribution
mbites$bites_binomial<-ifelse(mbites$bite_marks>50,50,mbites$bite_marks)

# Additional lines to process and make sure the data is not characters or no-integer data or anything like that
bite_out<-mbites[which(is.na(mbites$bites_binomial)==F),]

mbit<-mbites[which(is.na(bite_out$Sample)==F),]

# Subset of the big brecken bite data that only is the craters site
craters<-subset(BB,BB$Site=="Craters") 

# The sample is the unique identifier for individual plants, so we can merge using this
# Merging together Marcella's data (raw bites) and Brecken's data (average bites, but values for chemistry)
craters=merge(craters,mbit,by.x="Sample",by.y="Sample") 

## Check out the dimensions of the input data:
# Bites
length(craters$Bites)
table(craters$Bites)
# Wide distribution of bites that are averaged across morphotype 

# Season
table(craters$Season)

# Species
table(craters$Species)

# Plant height 
table(craters$PlantSize)

table(craters$PatchType)

table(craters$Patch_ID.x)[-which(table(craters$Patch_ID.x)==0)]  

# Standardize our covariates
craters$CP_Pred_std<-stdize(craters$CP_Pred)
craters$Phenolics_Pred_std<-stdize(craters$Phenolics_Pred)
craters$Monoterpenes_Pred_std<-stdize(craters$Monoterpenes_Pred)

craters$CP_Ref_std<-stdize(craters$CP_Ref)
craters$Phenolics_Ref_std<-stdize(craters$Phenolics_Ref)
craters$Monoterpenes_Ref_std<-stdize(craters$Monoterpenes_Ref)

craters$Patch_ID<-droplevels(as.factor(paste("p",craters$Patch_ID.x,sep="_")))

craters_use<-na.omit(data.frame(Bites=craters$bites_binomial, CP_Pred_std=craters$CP_Pred_std,PatchType=craters$Patch_ID,Phenolics_Pred_std=craters$Phenolics_Pred_std,Monoterpenes_Pred_std=craters$Monoterpenes_Pred_std,Patch_ID=craters$Patch_ID,CP_Ref_std=craters$CP_Ref_std,Phenolics_Ref_std=craters$Phenolics_Ref_std, Monoterpenes_Ref_std=craters$Monoterpenes_Ref_std))
                                
# Creating a proportional variable to help visualize the data
craters_use$bprop<-craters_use$Bites/50 #since 50 is the max

# This is a how binomial proportional data are read into R
# This is creating a matrix with the two important details for binomial regression the number of 
#successes and the number of failures. 
craters_bound<-cbind(craters_use$Bites,50-craters_use$Bites)
craters_use$craters_bound<-craters_bound

## Check out the dimensions of the final data:
# Bites
length(craters_use$Bites)
table(craters_use$Bites)
# 162 out of 244 bites are zero.

# Season
table(craters_use$Season)
# Winter only

# Patch type
table(craters_use$PatchType)
# Patch type is now patch ID

min(craters_use$CP_Ref_std) 
max(craters_use$CP_Ref_std) 

min(craters_use$CP_Pred_std) 
max(craters_use$CP_Pred_std) 

min(craters_use$Phenolics_Ref_std) 
max(craters_use$Phenolics_Ref_std) 

min(craters_use$Phenolics_Pred_std) 
max(craters_use$Phenolics_Pred_std) 

min(craters_use$Monoterpenes_Ref_std) 
max(craters_use$Monoterpenes_Ref_std) 

min(craters_use$Monoterpenes_Pred_std) 
max(craters_use$Monoterpenes_Pred_std) 

##Descriptive Stats

# Crude Proteins

mean(craters$CP_Ref, na.rm=TRUE) 
sd(craters$CP_Ref, na.rm=TRUE) 

mean(craters$CP_Pred, na.rm=TRUE) 
sd(craters$CP_Pred, na.rm=TRUE)

mean(craters_use$CP_Ref_std, na.rm=TRUE)
sd(craters_use$CP_Ref_std, na.rm=TRUE)

mean(craters_use$CP_Pred_std, na.rm=TRUE)
sd(craters_use$CP_Pred_std, na.rm=TRUE)

# Monoterpenes
mean(craters$Monoterpenes_Ref, na.rm=TRUE)
sd(craters$Monoterpenes_Ref, na.rm=TRUE)

mean(craters$Monoterpenes_Pred, na.rm=TRUE)
sd(craters$Monoterpenes_Pred, na.rm=TRUE)

mean(craters_use$Monoterpenes_Ref_std, na.rm=TRUE)
sd(craters_use$Monoterpenes_Ref_std, na.rm=TRUE)

mean(craters_use$Monoterpenes_Pred_std, na.rm=TRUE)
sd(craters_use$Monoterpenes_Pred_std, na.rm=TRUE)

# Phenolics
mean(craters$Phenolics_Ref, na.rm=TRUE)
sd(craters$Phenolics_Ref, na.rm=TRUE)

mean(craters$Phenolics_Pred, na.rm=TRUE)
sd(craters$Phenolics_Pred, na.rm=TRUE)

mean(craters_use$Phenolics_Ref_std, na.rm=TRUE)
sd(craters_use$Phenolics_Ref_std, na.rm=TRUE)

mean(craters_use$Phenolics_Pred_std, na.rm=TRUE)
sd(craters_use$Phenolics_Pred_std, na.rm=TRUE)

```

# Question 1: what are the effects of chemistry on bites?

```{r}

mREF_Craters_single <- rstanarm::stan_glmer(craters_bound~CP_Ref_std+Phenolics_Ref_std+Monoterpenes_Ref_std+(1|Patch_ID),data=craters_use,cores=4,family="binomial",iter=10000)

png(file="./Craters_Reference.png")
summary(mREF_Craters_single)
plot(mREF_Craters_single,regex_pars="_std")
dev.off()

save(mREF_Craters_single,file="mREF_Craters_single.Rdata")

##############
# Extract posteriors

Craters_single_REF <- as.data.frame(mREF_Craters_single)

Phenolics_out <- Craters_single_REF$Phenolics_Ref_std
Phenolics_REF_cat <- rep("Phenolics_REF",times=length(Phenolics_out))

CP_out <- Craters_single_REF$CP_Ref_std
CP_REF_cat <- rep("CP_REF",times=length(CP_out))

Monoterpenes_out <- Craters_single_REF$Monoterpenes_Ref_std
Monoterpenes_REF_cat <- rep("Monoterpenes_REF",times=length(Monoterpenes_out))

pos_draws <- c(Phenolics_out,CP_out,Monoterpenes_out)

chem_type <- c(Phenolics_REF_cat,CP_REF_cat,Monoterpenes_REF_cat)

Craters_single_REF <- data.frame(pos_draws,chem_type)

Craters_single_REF$Site<-rep("Craters",times=nrow(Craters_single_REF))

save(Craters_single_REF,file = "Craters_single_REF.Rdata")

```

# Question 2: does inference on chemistry effects change when using predicted, rather than observed values?

```{r}

mPRED_Craters_single <- rstanarm::stan_glmer(craters_bound~CP_Pred_std+Phenolics_Pred_std+Monoterpenes_Pred_std +(1|Patch_ID),data=craters_use,cores=4,family="binomial",iter=10000)

png(file="./Craters_Predicted.png")
summary(mPRED_Craters_single)
plot(mPRED_Craters_single,regex_pars="Pred")

save(mPRED_Craters_single,file="mPRED_Craters_single.Rdata")

##############
# Extract posteriors

Craters_single_PRED <- as.data.frame(mPRED_Craters_single)

Phenolics_out <- Craters_single_PRED$Phenolics_Pred_std
Phenolics_PRED_cat <- rep("Phenolics_PRED",times=length(Phenolics_out))

CP_out <- Craters_single_PRED$CP_Pred_std
CP_PRED_cat <- rep("CP_PRED",times=length(CP_out))

Monoterpenes_out <- Craters_single_PRED$Monoterpenes_Pred_std
Monoterpenes_PRED_cat <- rep("Monoterpenes_PRED",times=length(CP_out))

pos_draws <- c(Phenolics_out,CP_out,Monoterpenes_out)

chem_type <- c(Phenolics_PRED_cat,CP_PRED_cat,Monoterpenes_PRED_cat)

Craters_single_PRED <- data.frame(pos_draws,chem_type)

Craters_single_PRED$Site<-rep("Craters",times=nrow(Craters_single_PRED))

save(Craters_single_PRED,file="Craters_single_PRED.Rdata")

```

#Question 3: how does the predictions changes when using obs vs predicted chemistry?

#https://onlinelibrary.wiley.com/doi/full/10.1111/ecog.02881
#paper that describes our leave-one-out approach

```{r}

# In this code, we are creating subsets of the data
craters_levs<-unique(craters_use$Patch_ID)
craters_in<-vector("list",length(craters_levs))
craters_out<-vector("list",length(craters_levs))

# We are testing three different models:
# Model 1 is the observed chemistry
# Model 2 is the predicted chemistry
# Model 3 is a null model with no chemistry
ref_preds<-vector("list",length(craters_levs))
pred_preds<-vector("list",length(craters_levs))
null_preds<-vector("list",length(craters_levs))

for(i in 1:length(craters_levs)) 
{

  # Patch ID out, running the model, and predicting on the left out patch
  
  # Data use to fit the model
  craters_in[[i]]<-craters_use[-which(craters_use$Patch_ID==craters_levs[i]),]
  
   # Data used to test the model
  craters_out[[i]]<-craters_use[which(craters_use$Patch_ID==craters_levs[i]),]
  
  m0_Craters<-stan_glmer(craters_bound~1+(1|Patch_ID),data=craters_in[[i]],cores=4, family = "binomial", iter=10000)
  
  # Making predictions for the left out data
  null_preds[[i]]=posterior_epred(m0_Craters,newdata=craters_out[[i]])
  
  mPred_Craters<-stan_glmer(craters_bound~CP_Pred_std+Phenolics_Pred_std+Monoterpenes_Pred_std+(1|Patch_ID),data=craters_in[[i]],cores=4, family = "binomial", iter=10000)
  
  pred_preds[[i]]=posterior_epred(mPred_Craters,newdata=craters_out[[i]])
  
  mREF_Craters<-stan_glmer(craters_bound~CP_Ref_std+Phenolics_Ref_std+Monoterpenes_Ref_std+(1|Patch_ID),data=craters_in[[i]],cores=4, family = "binomial", iter=10000)
  
  ref_preds[[i]]<-posterior_epred(mREF_Craters,newdata=craters_out[[i]])
  }

null_preds_t<-t(null_preds)

# Extracting the predictions
# Binding the results together in a single data frame
craters_logo<-vector("list",4)
names(craters_logo)<-c("out_data","null","ref","pred")
craters_logo[[1]]<-do.call("rbind",craters_out)
craters_logo[[2]]<-t(do.call("cbind",null_preds))
craters_logo[[3]]<-t(do.call("cbind",ref_preds))
craters_logo[[4]]<-t(do.call("cbind",pred_preds))

# Save the object 
save(craters_logo,file="craters_logo.Rdata")

load(file="craters_logo.Rdata")
str(craters_logo)

# Predicted data
# These are the predictions from the three models above. These are matrices, because we are doing this in a Bayesian context. 
null_preds=craters_logo$null
ref_preds=craters_logo$ref
pred_preds=craters_logo$pred

# New variable
craters_obs<-craters_logo$out_data$craters_bound[,1]

# New variable

craters_total <- craters_logo$out_data$craters_bound[,2]

craters_null<-apply(null_preds,1,mean)
length(craters_null)
craters_ref<-apply(ref_preds,1,mean)
length(craters_ref)
craters_pred<-apply(pred_preds,1,mean)
length(craters_pred)

# Likelihood of observed data, given predicted data. We're looking for the lowest number here (this is a call to the probability distribution = how rampant a likely variable is.

-sum(dbinom(craters_obs,prob=craters_ref/craters_total,size=50,log=T),na.rm=T)
-sum(dbinom(craters_obs,prob=craters_null/craters_total,size=50,log=T),na.rm=T)
-sum(dbinom(craters_obs,prob=craters_pred/craters_total,size=50,log=T),na.rm=T)

# Mean absolute error, defined above. This is on the scale of the data, so the negative log likelihoods (which are a bit abstract) make more sense. 
mae(craters_null,craters_obs) # Run these for all columns of the posterior estimates of mae, and then apply the 95%CI to this).
mae(craters_ref,craters_obs)
mae(craters_pred, craters_obs)

```

# General posterior draw descriptive statistics

```{r}

nameo <- list.files()[-1]

chem_range <- read.csv("Text_Chemistry_Mins_Max_13July2023.csv", header=TRUE)

load("mREF_Craters_single.Rdata")
load("mPRED_Craters_single.Rdata")

# All chemicals
chemm <- read.csv("Text_Chemistry_Mins_Max_13July2023.csv", header=TRUE)

ref_craters_posteriors <- data.frame(mREF_Craters_single)
pred_craters_posteriors <- data.frame(mPRED_Craters_single)

dim(ref_craters_posteriors)
dim(pred_craters_posteriors)

```

# Probability of Direction - Reference Chemistry

What is the percentage of draws that are either positive of negative?

```{r}

# Crude Proteins
length(which(ref_craters_posteriors$CP_Ref_std>0))/length(ref_craters_posteriors$CP_Ref_std)

length(which(ref_craters_posteriors$CP_Ref_std<0))/length(ref_craters_posteriors$CP_Ref_std)

# Monoterpenes
length(which(ref_craters_posteriors$Monoterpenes_Ref_std>0))/length(ref_craters_posteriors$Monoterpenes_Ref_std)
 
length(which(ref_craters_posteriors$Monoterpenes_Ref_std<0))/length(ref_craters_posteriors$Monoterpenes_Ref_std)

# Phenolics
length(which(ref_craters_posteriors$Phenolics_Ref_std>0))/length(ref_craters_posteriors$Phenolics_Ref_std)
length(which(ref_craters_posteriors$Phenolics_Ref_std<0))/length(ref_craters_posteriors$Phenolics_Ref_std)

```

# Probability of Direction - Predicted Chemistry

What is the percentage of draws that are either positive of negative?

Note that we never report probabilities of 100% in papers--instead write >99%

```{r}

# Crude Proteins
length(which(pred_craters_posteriors$CP_Pred_std>0))/length(pred_craters_posteriors$CP_Pred_std)
 
length(which(pred_craters_posteriors$CP_Pred_std<0))/length(pred_craters_posteriors$CP_Pred_std)

# Monoterpenes
length(which(pred_craters_posteriors$Monoterpenes_Pred_std>0))/length(pred_craters_posteriors$Monoterpenes_Pred_std)

length(which(pred_craters_posteriors$Monoterpenes_Pred_std<0))/length(pred_craters_posteriors$Monoterpenes_Pred_std)

# Phenolics
length(which(pred_craters_posteriors$Phenolics_Pred_std>0))/length(pred_craters_posteriors$Phenolics_Pred_std)

length(which(pred_craters_posteriors$Phenolics_Pred_std<0))/length(pred_craters_posteriors$Phenolics_Pred_std)

```

# Effect Size Min & Max - Reference Chemistry

```{r}

# Referencing min and max from data frame
chemm$Ref_Min[which(chemm$Site=="Craters" & chemm$Chemical=="Crude Protein")] 
chemm$Ref_Max[which(chemm$Site=="Craters" & chemm$Chemical=="Crude Protein")] 

# Setting up an empty vector to fill in with predictions
predicted_diff_cp_ref <- rep(NA,times=ncol(ref_craters_posteriors))
predicted_diff_Monoterpenes_ref <- rep(NA,times=ncol(ref_craters_posteriors))
predicted_diff_Phenolics_ref <- rep(NA,times=ncol(ref_craters_posteriors))

# CP
for(i in 1:ncol(ref_craters_posteriors)){

# This is just an intercept + slope*x. plogis ensures it is a probability. We are looping over every value of the posterior draw to propagate uncertainty.
min_pred<-plogis(ref_craters_posteriors$X.Intercept.[i]+ref_craters_posteriors$CP_Ref_std[i]*chemm$Ref_Min[which(chemm$Site=="Craters" & chemm$Chemical=="Crude Protein")])
  
max_pred<-plogis(ref_craters_posteriors$X.Intercept.[i]+ref_craters_posteriors$CP_Ref_std[i]*chemm$Ref_Max[which(chemm$Site=="Craters" & chemm$Chemical=="Crude Protein")])
  
predicted_diff_cp_ref[i]<-max_pred-min_pred #This is the difference we will store.
  }  

quantile(predicted_diff_cp_ref,c(0.025,0.5,0.975)) 

# Monoterpenes
for(i in 1:ncol(ref_craters_posteriors)){

# This is just an intercept + slope*x. plogis ensures it is a probability. We are looping over every value of the posterior draw to propagate uncertainty.
min_pred<-plogis(ref_craters_posteriors$X.Intercept.[i]+ref_craters_posteriors$Monoterpenes_Ref_std[i]*chemm$Ref_Min[which(chemm$Site=="Craters" & chemm$Chemical=="Monoterpenes")])
  
max_pred<-plogis(ref_craters_posteriors$X.Intercept.[i]+ref_craters_posteriors$Monoterpenes_Ref_std[i]*chemm$Ref_Max[which(chemm$Site=="Craters" & chemm$Chemical=="Monoterpenes")])
  
predicted_diff_Monoterpenes_ref[i]<-max_pred-min_pred #This is the difference we will store. 
}  

quantile(predicted_diff_Monoterpenes_ref,c(0.025,0.5,0.975)) 

# Phenolics
for(i in 1:ncol(ref_craters_posteriors)){

# This is just an intercept + slope*x. plogis ensures it is a probability. We are looping over every value of the posterior draw to propagate uncertainty.
min_pred<-plogis(ref_craters_posteriors$X.Intercept.[i]+ref_craters_posteriors$Phenolics_Ref_std[i]*chemm$Ref_Min[which(chemm$Site=="Craters" & chemm$Chemical=="Phenolics")])
  
max_pred<-plogis(ref_craters_posteriors$X.Intercept.[i]+ref_craters_posteriors$Phenolics_Ref_std[i]*chemm$Ref_Max[which(chemm$Site=="Craters" & chemm$Chemical=="Phenolics")])
  
predicted_diff_Phenolics_ref[i]<-max_pred-min_pred #This is the difference we will store.
}  

quantile(predicted_diff_Phenolics_ref,c(0.025,0.5,0.975)) 

```

# Effect Size Min & Max - Predicted Chemistry

```{r}

# Referencing min and max from data frame
chemm$Pred_Min[which(chemm$Site=="Craters" & chemm$Chemical=="Crude Protein")] 
chemm$Pred_Max[which(chemm$Site=="Craters" & chemm$Chemical=="Crude Protein")] 

# Setting up an empty vector to fill in with predictions
predicted_diff_cp_pred <- rep(NA,times=ncol(pred_craters_posteriors))
predicted_diff_Monoterpenes_pred <- rep(NA,times=ncol(pred_craters_posteriors))
predicted_diff_Phenolics_pred <- rep(NA,times=ncol(pred_craters_posteriors))

# CP
for(i in 1:ncol(pred_craters_posteriors)){

# This is just an intercept + slope*x. plogis ensures it is a probability. We are looping over every value of the posterior draw to propagate uncertainty.
min_pred<-plogis(pred_craters_posteriors$X.Intercept.[i]+pred_craters_posteriors$CP_Pred_std[i]*chemm$Pred_Min[which(chemm$Site=="Craters" & chemm$Chemical=="Crude Protein")])
  
max_pred<-plogis(pred_craters_posteriors$X.Intercept.[i]+pred_craters_posteriors$CP_Pred_std[i]*chemm$Pred_Max[which(chemm$Site=="Craters" & chemm$Chemical=="Crude Protein")])
  
predicted_diff_cp_pred[i]<-max_pred-min_pred #This is the difference we will store.
  }  

quantile(predicted_diff_cp_pred,c(0.025,0.5,0.975)) 

# Monoterpenes
for(i in 1:ncol(pred_craters_posteriors)){

# This is just an intercept + slope*x. plogis ensures it is a probability. We are looping over every value of the posterior draw to propagate uncertainty.
min_pred<-plogis(pred_craters_posteriors$X.Intercept.[i]+pred_craters_posteriors$Monoterpenes_Pred_std[i]*chemm$Pred_Min[which(chemm$Site=="Craters" & chemm$Chemical=="Monoterpenes")])
  
max_pred<-plogis(pred_craters_posteriors$X.Intercept.[i]+pred_craters_posteriors$Monoterpenes_Pred_std[i]*chemm$Pred_Max[which(chemm$Site=="Craters" & chemm$Chemical=="Monoterpenes")])
  
predicted_diff_Monoterpenes_pred[i]<-max_pred-min_pred #This is the difference we will store.
}  

quantile(predicted_diff_Monoterpenes_pred,c(0.025,0.5,0.975)) 

# Phenolics
for(i in 1:ncol(pred_craters_posteriors)){

# This is just an intercept + slope*x. plogis ensures it is a probability. We are looping over every value of the posterior draw to propagate uncertainty.
min_pred<-plogis(pred_craters_posteriors$X.Intercept.[i]+pred_craters_posteriors$Phenolics_Pred_std[i]*chemm$Pred_Min[which(chemm$Site=="Craters" & chemm$Chemical=="Phenolics")])
  
max_pred<-plogis(pred_craters_posteriors$X.Intercept.[i]+pred_craters_posteriors$Phenolics_Pred_std[i]*chemm$Pred_Max[which(chemm$Site=="Craters" & chemm$Chemical=="Phenolics")])
  
predicted_diff_Phenolics_pred[i]<-max_pred-min_pred 
}  

quantile(predicted_diff_Phenolics_pred,c(0.025,0.5,0.975)) 

```

