---
title: "Chapter 2 - Bite Data - Chemistry - Predicted Chemistry at JN Magic"
output:
  pdf_document: default
  html_document: default
---

This R Markdown file will input data for the JN Magic site (Magic = Camas Prairie) and prepare it for three downstream analyses determining the effects of chemistry and predicted chemistry on bite data. 

JN Magic is a pygmy rabbit site that underwent stratified random collection of data, with 3-6 plants sampled per patch and patches randomly selected within distance strata for dist to burrow (0-20m; 20-40m; 40-100m). While data points include a combination of individual plants and pooled samples, only the individual plant samples were used. Data was collected in Summer and Winter, and had no upper limit for the number of bites counted. A negative binomial distribution was used to analyze this data set. 

In addition to these data, individual pellet counts within a meter of each individual shrub. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#Load libraries
library("rprojroot")
library("loo")
library("rstanarm")
options(mc.cores = parallel::detectCores())
library("ggplot2")
library("bayesplot")
theme_set(bayesplot::theme_default(base_family = "sans"))
library("MASS")
library("lme4")
library("brms")
library("rstanarm")

```

# Functions

These functions are used throughout the markdown, and include ways for evaluating predictive error and standardizing the inputs. 

## Root mean square error (RSME)
This shows the difference between an estimator and the values observed, and provides a measure of accuracy.

## Mean absolute error (MAE)
This is a measure of errors between paired observations expressing the same phenomenon, and is one of a number of ways of comparing forecasts with their eventual outcomes.

## Residual sum of squares (RSS)
This is a measure of discrepancy between the data (x) and the model (d). A small value indicates a good fit between the data and the model (0 is a perfect fit). This number can be infinite, as far as I'm aware.

## Total sum of squares (TSS)

This is the explained sum of squares plus the RSS. 

## R2

The proportion of variance explained by the model out of the total variance in the data (0-1). Closer to one means 100% fit. 

## splt

Tidies up the data by removing the double names

## stdize

Putting all of the covariates on the same scale 
http://www.stat.columbia.edu/~gelman/research/published/standardizing7.pdf


```{r}
# This first function is for root mean square, where m is the model predictions, and x is the data.
rmse <- function(m,x) 
{
  sqrt(mean((x-m)^2,na.rm=T))
}

# This function is for mean absolute error, where m is the model predictions, and x is the data. 
mae <- function(m,x)
{
  mean(abs(((x-m))),na.rm=T)
}

# This function is for residual sum of squares
RSS <- function(m,x) 
{
  sum((((m))-(x))^2)
}

# This function is for total sum of squares
TSS <- function(x) 
{
  sum(((x)-(mean(x)))^2)
  }

R2<-function(m,x,logo=F) {
  mors<-na.omit(data.frame(m,x))
  m<-mors$m
  x<-mors$x
  
  if(logo==F) {return(1-RSS(m,x)/TSS(x))} else {return(1-RSS1(m,x)/TSS1(x))}
}

# Split names
splt=function(x,split,num) {
  
  x<-as.character(x)
  p1=strsplit(x,split=split,fixed=T)
  p2=unlist(lapply(p1,"[",num))
  return(p2)
}

# Standardize covariates
stdize<-function(x) {(x-mean(x,na.rm=T))/(2*sd(x,na.rm=T))}

```

# Read in Files

```{r}

# Main data set that includes all the sites, chemotype levels. We're setting periods and blank spaces to read in to R as NA:
Phenolics <- read.csv("Phenolics.csv", na.strings=c("."," ","","NA"))
Monoterpenes <- read.csv("Monoterpenes.csv", na.strings=c("."," ","","NA"))
Crude_Protein <- read.csv("Crude_protein.csv", na.strings=c("."," ","","NA"))

# Subset datasets to sites:
JN_Magic_P <-subset(Phenolics,Phenolics$Site=="JNMagic") 
JN_Magic_M <-subset(Monoterpenes, Monoterpenes$Site=="JNMagic") 
JN_Magic_CP <-subset(Crude_Protein,Crude_Protein$Site=="JNMagic") 

# See the distribution of number of bites. You'll see there is no averaged data here. 
unique(JN_Magic_P$Bites)
unique(JN_Magic_M$Bites)
unique(JN_Magic_CP$Bites)

## Check out the dimensions of the input data:
# Bites
length(JN_Magic_P$Bites) #531
table(JN_Magic_P$Bites)

length(JN_Magic_M$Bites) #578 
table(JN_Magic_M$Bites)

length(JN_Magic_CP$Bites) #587
table(JN_Magic_CP$Bites)

# Season
table(JN_Magic_P$Season) #summer 290 #winter 241 
table(JN_Magic_M$Season) #summer 334 #winter 244 
table(JN_Magic_CP$Season) #summer 343 #winter 244 

# Species
table(JN_Magic_P$Species) #dwarf 97, dwarf_comp 41, wyo_comp 108, wyoming 285
table(JN_Magic_M$Species) #dwarf 104, dwarf_comp 44, wyo_comp 116, wyoming 314
table(JN_Magic_CP$Species) #dwarf 107, dwarf_comp 46, wyo_comp 115, wyoming 319

# Plant height
table(JN_Magic_P$PlantSize) #table of extent 0
table(JN_Magic_M$PlantSize) #table of extent 0
table(JN_Magic_CP$PlantSize) #table of extent 0
# Not available at this site

# Patch type
table(JN_Magic_P$PatchType) #dwarf 138, off 201, on 192
table(JN_Magic_M$PatchType) #dwarf 148, off 210, on 220
table(JN_Magic_CP$PatchType) #dwarf 153, off 210, on 224

# Patch_ID here is the random effect
table(JN_Magic_P$Patch_ID)[-which(table(JN_Magic_P$Patch_ID)==0)] #named integer(0)
table(JN_Magic_M$Patch_ID)[-which(table(JN_Magic_M$Patch_ID)==0)] #named integer(0)
table(JN_Magic_CP$Patch_ID)[-which(table(JN_Magic_CP$Patch_ID)==0)] #named integer(0)

# Standardize our covariates
JN_Magic_CP$CP_Pred_std<-stdize(JN_Magic_CP$CP_newpred)
JN_Magic_P$Phenolics_Pred_std<-stdize(JN_Magic_P$Phenolics_newpred)
JN_Magic_M$Monoterpenes_Pred_std<-stdize(JN_Magic_M$Monoterpenes_newpred)

JN_Magic_CP$CP_Ref_std<-stdize(JN_Magic_CP$CP_Ref)
JN_Magic_P$Phenolics_Ref_std<-stdize(JN_Magic_P$Phenolics_Ref)
JN_Magic_M$Monoterpenes_Ref_std<-stdize(JN_Magic_M$Monoterpenes_Ref)

JN_Magic_CP$Patch_ID<-droplevels(as.factor(paste("p",JN_Magic_CP$Patch_ID,sep="_")))
JN_Magic_P$Patch_ID<-droplevels(as.factor(paste("p",JN_Magic_P$Patch_ID,sep="_")))
JN_Magic_M$Patch_ID<-droplevels(as.factor(paste("p",JN_Magic_M$Patch_ID,sep="_")))

# Create the data set that we use moving forward
JN_Magic_P_use<-na.omit(data.frame(Bites=JN_Magic_P$Bites,PatchType=JN_Magic_P$PatchType,Season=JN_Magic_P$Season, Phenolics_Pred_std=JN_Magic_P$Phenolics_Pred_std,Patch_ID=JN_Magic_P$Patch_ID, Phenolics_Ref_std=JN_Magic_P$Phenolics_Ref_std))

JN_Magic_M_use<-na.omit(data.frame(Bites=JN_Magic_M$Bites,PatchType=JN_Magic_M$PatchType,Season=JN_Magic_M$Season, Monoterpenes_Pred_std=JN_Magic_M$Monoterpenes_Pred_std,Patch_ID=JN_Magic_M$Patch_ID, Monoterpenes_Ref_std=JN_Magic_M$Monoterpenes_Ref_std))

JN_Magic_CP_use<-na.omit(data.frame(Bites=JN_Magic_CP$Bites,PatchType=JN_Magic_CP$PatchType,Season=JN_Magic_CP$Season,CP_Pred_std=JN_Magic_CP$CP_Pred_std,Patch_ID=JN_Magic_CP$Patch_ID, CP_Ref_std=JN_Magic_CP$CP_Ref_std))

# If bites >0, then 1. If not, 0 (creating a binomial distribution)
JN_Magic_P_use$Bites_Binomial <- ifelse(JN_Magic_P_use$Bites > 0, 1, 0)
JN_Magic_M_use$Bites_Binomial <- ifelse(JN_Magic_M_use$Bites > 0, 1, 0)
JN_Magic_CP_use$Bites_Binomial <- ifelse(JN_Magic_CP_use$Bites > 0, 1, 0)

## Check out the dimensions of the final data:
# Bites
length(JN_Magic_P_use$Bites_Binomial) #382
table(JN_Magic_P_use$Bites)

length(JN_Magic_M_use$Bites_Binomial) #418
table(JN_Magic_M_use$Bites)

length(JN_Magic_CP_use$Bites_Binomial) #426
table(JN_Magic_CP_use$Bites)

# Season
table(JN_Magic_P_use$Season) #summer 215, winter 167
table(JN_Magic_M_use$Season) #summer 247, winter 171
table(JN_Magic_CP_use$Season) #summer 255, winter 171

# Patch type
table(JN_Magic_P_use$PatchType) #dwarf 97, off 146, on 139
table(JN_Magic_M_use$PatchType) #dwarf 104, off 154, on 160
table(JN_Magic_CP_use$PatchType) #dwarf 107, off 155, on 164

#Mins and Maxes

min(JN_Magic_P_use$Phenolics_Ref_std) #-0.7762658
max(JN_Magic_P_use$Phenolics_Ref_std) #3.383833
min(JN_Magic_P_use$Phenolics_Pred_std) #-1.376069
max(JN_Magic_P_use$Phenolics_Pred_std) #1.392438

min(JN_Magic_M_use$Monoterpenes_Ref_std) #-1.020171
max(JN_Magic_M_use$Monoterpenes_Ref_std) #1.913172
min(JN_Magic_M_use$Monoterpenes_Pred_std) #-1.153206
max(JN_Magic_M_use$Monoterpenes_Pred_std) #1.281484

min(JN_Magic_CP_use$CP_Ref_std) #-3.144783
max(JN_Magic_CP_use$CP_Ref_std) #1.785229
min(JN_Magic_CP_use$CP_Pred_std) #-1.558475
max(JN_Magic_CP_use$CP_Pred_std) #1.877752

## Descriptive Stats

# Phenolics
mean(JN_Magic_P$Phenolics_Ref, na.rm=TRUE) #10.94627
sd(JN_Magic_P$Phenolics_Ref, na.rm=TRUE) #6.084433
mean(JN_Magic_P$Phenolics_newpred, na.rm=TRUE) #11.15397
sd(JN_Magic_P$Phenolics_newpred, na.rm=TRUE) #4.386831

mean(JN_Magic_P_use$Phenolics_Ref_std, na.rm=TRUE) #-0.00351068
sd(JN_Magic_P_use$Phenolics_Ref_std, na.rm=TRUE) #0.5331163
mean(JN_Magic_P_use$Phenolics_Pred_std, na.rm=TRUE) #-0.008021606
sd(JN_Magic_P_use$Phenolics_Pred_std, na.rm=TRUE) #0.5114148

# Monoterpenes
mean(JN_Magic_M$Monoterpenes_Ref, na.rm=TRUE) #787.6531
sd(JN_Magic_M$Monoterpenes_Ref, na.rm=TRUE) #332.5367
mean(JN_Magic_M$Monoterpenes_newpred, na.rm=TRUE) #790.5258
sd(JN_Magic_M$Monoterpenes_newpred, na.rm=TRUE) #306.3466

mean(JN_Magic_M_use$Monoterpenes_Ref_std, na.rm=TRUE) #-0.006749789
sd(JN_Magic_M_use$Monoterpenes_Ref_std, na.rm=TRUE) #0.5160459
mean(JN_Magic_M_use$Monoterpenes_Pred_std, na.rm=TRUE) #0.003263942
sd(JN_Magic_M_use$Monoterpenes_Pred_std, na.rm=TRUE) #0.5185673

# Crude Proteins
mean(JN_Magic_CP$CP_Ref, na.rm=TRUE) #10.32099
sd(JN_Magic_CP$CP_Ref, na.rm=TRUE) #1.64097
mean(JN_Magic_CP$CP_newpred, na.rm=TRUE) #10.32401
sd(JN_Magic_CP$CP_newpred, na.rm=TRUE) #1.217685

mean(JN_Magic_CP_use$CP_Ref_std, na.rm=TRUE) #0.008925703
sd(JN_Magic_CP_use$CP_Ref_std, na.rm=TRUE) #0.5228426
mean(JN_Magic_CP_use$CP_Pred_std, na.rm=TRUE) #0.02435716
sd(JN_Magic_CP_use$CP_Pred_std, na.rm=TRUE) #0.5136612


```

# Question 1: what are the effects of chemistry on bites?

```{r}

mREF_JN_Magic_single_P <-rstanarm::stan_glmer(Bites_Binomial~Season+Phenolics_Ref_std+(1|Patch_ID),data=JN_Magic_P_use,cores=4, family="binomial", iter=10000)

mREF_JN_Magic_single_M <-rstanarm::stan_glmer(Bites_Binomial~Season+Monoterpenes_Ref_std+(1|Patch_ID),data=JN_Magic_M_use,cores=4, family="binomial", iter=10000)

mREF_JN_Magic_single_CP <-rstanarm::stan_glmer(Bites_Binomial~Season+CP_Ref_std+(1|Patch_ID),data=JN_Magic_CP_use,cores=4, family="binomial", iter=10000)

png(file="./JN_Magic_Reference_P.png")
summary(mREF_JN_Magic_single_P)
plot(mREF_JN_Magic_single_P,regex_pars="_std")
dev.off()
save(mREF_JN_Magic_single_P, file = "mREF_JN_Magic_single_P.Rdata")

png(file="./JN_Magic_Reference_M.png")
summary(mREF_JN_Magic_single_M)
plot(mREF_JN_Magic_single_M,regex_pars="_std")
dev.off()
save(mREF_JN_Magic_single_M, file = "mREF_JN_Magic_single_M.Rdata")

png(file="./JN_Magic_Reference_CP.png")
summary(mREF_JN_Magic_single_CP)
plot(mREF_JN_Magic_single_CP,regex_pars="_std")
dev.off()
save(mREF_JN_Magic_single_CP, file = "mREF_JN_Magic_single_CP.Rdata")

##############
# Extract posteriors

JN_Magic_single_ref_P <- as.data.frame(mREF_JN_Magic_single_P)
Phenolics_out <- JN_Magic_single_ref_P$Phenolics_Ref_std
Phenolics_ref_cat <- rep("Phenolics_ref",times=length(Phenolics_out))

JN_Magic_single_ref_M <- as.data.frame(mREF_JN_Magic_single_M)
Monoterpenes_out <- JN_Magic_single_ref_M$Monoterpenes_Ref_std
Monoterpenes_ref_cat <- rep("Monoterpenes_ref",times=length(Monoterpenes_out))

JN_Magic_single_ref_CP <- as.data.frame(mREF_JN_Magic_single_CP)
CP_out <- JN_Magic_single_ref_CP$CP_Ref_std
CP_ref_cat <- rep("CP_ref",times=length(CP_out))

pos_draws <- c(Phenolics_out,CP_out,Monoterpenes_out)

chem_type <- c(Phenolics_ref_cat,CP_ref_cat, Monoterpenes_ref_cat)

JN_Magic_single_ref <- data.frame(pos_draws,chem_type)

JN_Magic_single_ref$Site<-rep("JN_Magic",times=nrow(JN_Magic_single_ref))

save(JN_Magic_single_ref,file="JN_Magic_single_ref.Rdata")

```

# Question 2: does inference on chemistry effects change when using predicted, rather than observed values?

```{r}

mPRED_JN_Magic_single_P <-rstanarm::stan_glmer(Bites_Binomial~Season+Phenolics_Pred_std+(1|Patch_ID),data=JN_Magic_P_use,cores=4, family="binomial", iter=10000)

mPRED_JN_Magic_single_M <-rstanarm::stan_glmer(Bites_Binomial~Season+Monoterpenes_Pred_std+(1|Patch_ID),data=JN_Magic_M_use,cores=4, family="binomial", iter=10000)

mPRED_JN_Magic_single_CP <-rstanarm::stan_glmer(Bites_Binomial~Season+CP_Pred_std+(1|Patch_ID),data=JN_Magic_CP_use,cores=4, family="binomial", iter=10000)

png(file="./JN_Magic_Pred_P.png")
summary(mPRED_JN_Magic_single_P)
plot(mPRED_JN_Magic_single_P,regex_pars="_std")
save(mPRED_JN_Magic_single_P, file = "mPRED_JN_Magic_single_P.Rdata")

png(file="./JN_Magic_Pred_M.png")
summary(mPRED_JN_Magic_single_M)
plot(mPRED_JN_Magic_single_M,regex_pars="_std")
save(mPRED_JN_Magic_single_M, file = "mPRED_JN_Magic_single_M.Rdata")

png(file="./JN_Magic_Pred_CP.png")
summary(mPRED_JN_Magic_single_CP)
plot(mPRED_JN_Magic_single_CP,regex_pars="_std")
save(mPRED_JN_Magic_single_CP, file = "mPRED_JN_Magic_single_CP.Rdata")

##############
# Extract posteriors

JN_Magic_single_pred_P <- as.data.frame(mPRED_JN_Magic_single_P)
Phenolics_out <- JN_Magic_single_pred_P$Phenolics_Pred_std
Phenolics_pred_cat <- rep("Phenolics_pred",times=length(Phenolics_out))

JN_Magic_single_pred_M <- as.data.frame(mPRED_JN_Magic_single_M)
Monoterpenes_out <- JN_Magic_single_pred_M$Monoterpenes_Pred_std
Monoterpenes_pred_cat <- rep("Monoterpenes_pred",times=length(Monoterpenes_out))

JN_Magic_single_pred_CP <- as.data.frame(mPRED_JN_Magic_single_CP)
CP_out <- JN_Magic_single_pred_CP$CP_Pred_std
CP_pred_cat <- rep("CP_pred",times=length(CP_out))

pos_draws <- c(Phenolics_out,CP_out,Monoterpenes_out)

chem_type <- c(Phenolics_pred_cat,CP_pred_cat,Monoterpenes_pred_cat)

JN_Magic_single_pred <- data.frame(pos_draws,chem_type)

JN_Magic_single_pred$Site<-rep("JN_Magic",times=nrow(JN_Magic_single_pred))

save(JN_Magic_single_pred,file="JN_Magic_single_pred.Rdata")

```

# Question 3: how does the predictions changes when using obs vs predicted chemistry?

# https://onlinelibrary.wiley.com/doi/full/10.1111/ecog.02881
#paper that describes our leave-one-out approach

```{r}

#####Phenolics

# In this code, we are creating subsets of the data
JN_Magic_levs_P <- unique(JN_Magic_P_use$Patch_ID)
JN_Magic_in_P <- vector("list",length(JN_Magic_levs_P))
JN_Magic_out_P <- vector("list",length(JN_Magic_levs_P))

# We are testing three different models:
# Model 1 is the observed chemistry
# Model 2 is the predicted chemistry
# Model 3 is a null model with no chemistry
ref_preds_P <- vector("list",length(JN_Magic_levs_P))
pred_preds_P <- vector("list",length(JN_Magic_levs_P))
null_preds_P <- vector("list",length(JN_Magic_levs_P))
#lists of predictions for each dataset

for(i in 1:length(JN_Magic_levs_P)) #JN_Magic_levs is the unique number of patch ids
{
  # For each one of if (!requireNamespace("devtools", quietly = TRUE)){install.packages("devtools")}   devtools::install_github("jbisanz/qiime2R")the patch ids, this is looping through.
  # If you want to trouble shoot this, put i = 1 into the r consul and run line by line. 
  # Patch id out, running the model, and predicting on the left out patch
  
  # Data use to fit the model
  JN_Magic_in_P[[i]] <- JN_Magic_P_use[-which(JN_Magic_P_use$Patch_ID==JN_Magic_levs_P[i]),]
  
   # Data used to test the model
  JN_Magic_out_P[[i]] <- JN_Magic_P_use[which(JN_Magic_P_use$Patch_ID==JN_Magic_levs_P[i]),]
  
  m0_JN_Magic_P <- stan_glmer(Bites_Binomial~Season+(1|Patch_ID),data=JN_Magic_in_P[[i]],cores=4, family = "binomial", iter=10000)
  
  # Making predictions for the left out data
  null_preds_P[[i]] <- posterior_epred(m0_JN_Magic_P,newdata=JN_Magic_out_P[[i]])
  
  mPRED_JN_Magic_P <- stan_glmer(Bites_Binomial~Season+Phenolics_Pred_std+(1|Patch_ID),data=JN_Magic_in_P[[i]],cores=4, family = "binomial",iter=10000)
  
  pred_preds_P[[i]] <- posterior_epred(mPRED_JN_Magic_P,newdata=JN_Magic_out_P[[i]])
  
  mREF_JN_Magic_P <- stan_glmer(Bites_Binomial~Season+Phenolics_Ref_std+(1|Patch_ID),data=JN_Magic_in_P[[i]],cores=4, family = "binomial",iter=10000)
  
  ref_preds_P[[i]] <- posterior_epred(mREF_JN_Magic_P,newdata=JN_Magic_out_P[[i]])
  }

null_preds_t <- t(null_preds_P)

# Extracting the predictions
# Binding the results together in a single data frame
JN_Magic_logo_P <- vector("list",4)
names(JN_Magic_logo_P) <- c("out_data","null","ref","pred")
JN_Magic_logo_P[[1]] <- do.call("rbind",JN_Magic_out_P)
JN_Magic_logo_P[[2]] <- t(do.call("cbind",null_preds_P))
JN_Magic_logo_P[[3]] <- t(do.call("cbind",ref_preds_P))
JN_Magic_logo_P[[4]] <- t(do.call("cbind",pred_preds_P))

# Save the object 
save(JN_Magic_logo_P,file="JN_Magic_logo_P.Rdata")

# Load(file="JN_Magic_logo.Rdata")
str(JN_Magic_logo_P)

# Predicted data
# These are the predictions from the three models above. These are matrices, because we are doing this in a Bayesian context. 
null_preds_P <- JN_Magic_logo_P$null
ref_preds_P <- JN_Magic_logo_P$ref
pred_preds_P <- JN_Magic_logo_P$pred

# New variable
JN_Magic_obs_P <- JN_Magic_logo_P$out_data$Bites

# New variable (not sure what this would be in JN_Magic)
JN_Magic_total_P <- JN_Magic_logo_P$out_data$Bites

# 1 = whether you're doing the mean across rows or columns
# Trying to predict across patchm, to create something in a list. 
JN_Magic_null_P <- apply(null_preds_P,1,mean)
length(JN_Magic_null_P) #382
JN_Magic_ref_P <- apply(ref_preds_P,1,mean)
length(JN_Magic_ref_P) #382
JN_Magic_pred_P <- apply(pred_preds_P,1,mean)
length(JN_Magic_pred_P) #382

# Likelihood of observed data, given predicted data. We're looking for the lowest number here (this is a call to the probability distribution = how rampant a likely variable is. Given the distribution how likely is it that we observe one value conditional on the probability of being bitten). Remember, we are avoiding over fitting by leaving out data. 

# Mean absolute error, defined above. This is on the scale of the data, so the negative log likelihoods (which are a bit abstract) make more sense. 
mae(JN_Magic_null_P,JN_Magic_obs_P) #Run these for all columns of the posterior estimates of mae, and then apply the 95%CI to this). #1.133652
mae(JN_Magic_ref_P,JN_Magic_obs_P) #1.1337
mae(JN_Magic_pred_P, JN_Magic_obs_P) #1.133909

#################Monoterpenes

# In this code, we are creating subsets of the data
JN_Magic_levs_M <- unique(JN_Magic_M_use$Patch_ID)
JN_Magic_in_M <- vector("list",length(JN_Magic_levs_M))
JN_Magic_out_M <- vector("list",length(JN_Magic_levs_M))

# We are testing three different models:
# Model 1 is the observed chemistry
# Model 2 is the predicted chemistry
# Model 3 is a null model with no chemistry
ref_preds_M <- vector("list",length(JN_Magic_levs_M))
pred_preds_M <- vector("list",length(JN_Magic_levs_M))
null_preds_M <- vector("list",length(JN_Magic_levs_M))
#lists of predictions for each dataset

for(i in 1:length(JN_Magic_levs_M)) #JN_Magic_levs is the unique number of patch ids
{
  # For each one of if (!requireNamespace("devtools", quietly = TRUE)){install.packages("devtools")}   devtools::install_github("jbisanz/qiime2R")the patch ids, this is looping through.
  # If you want to trouble shoot this, put i = 1 into the r consul and run line by line. 
  # Patch id out, running the model, and predicting on the left out patch
  
  # Data use to fit the model
  JN_Magic_in_M[[i]] <- JN_Magic_M_use[-which(JN_Magic_M_use$Patch_ID==JN_Magic_levs_M[i]),]
  
   # Data used to test the model
  JN_Magic_out_M[[i]] <- JN_Magic_M_use[which(JN_Magic_M_use$Patch_ID==JN_Magic_levs_M[i]),]
  
  m0_JN_Magic_M <- stan_glmer(Bites_Binomial~Season+(1|Patch_ID),data=JN_Magic_in_M[[i]],cores=4, family = "binomial", iter=10000)
  
  # Making predictions for the left out data
  null_preds_M[[i]] <- posterior_epred(m0_JN_Magic_M,newdata=JN_Magic_out_M[[i]])
  
  mPRED_JN_Magic_M <- stan_glmer(Bites_Binomial~Season+Monoterpenes_Pred_std+(1|Patch_ID),data=JN_Magic_in_M[[i]],cores=4, family = "binomial",iter=10000)
  
  pred_preds_M[[i]] <- posterior_epred(mPRED_JN_Magic_M,newdata=JN_Magic_out_M[[i]])
  
  mREF_JN_Magic_M <- stan_glmer(Bites_Binomial~Season+Monoterpenes_Ref_std+(1|Patch_ID),data=JN_Magic_in_M[[i]],cores=4, family = "binomial",iter=10000)
  
  ref_preds_M[[i]] <- posterior_epred(mREF_JN_Magic_M,newdata=JN_Magic_out_M[[i]])
  }

null_preds_t <- t(null_preds_M)

# Extracting the predictions
# Binding the results together in a single data frame
JN_Magic_logo_M <- vector("list",4)
names(JN_Magic_logo_M) <- c("out_data","null","ref","pred")
JN_Magic_logo_M[[1]] <- do.call("rbind",JN_Magic_out_M)
JN_Magic_logo_M[[2]] <- t(do.call("cbind",null_preds_M))
JN_Magic_logo_M[[3]] <- t(do.call("cbind",ref_preds_M))
JN_Magic_logo_M[[4]] <- t(do.call("cbind",pred_preds_M))

# Save the object 
save(JN_Magic_logo_M,file="JN_Magic_logo_M.Rdata")

# Load(file="JN_Magic_logo.Rdata")
str(JN_Magic_logo_M)

# Predicted data
# These are the predictions from the three models above. These are matrices, because we are doing this in a Bayesian context. 
null_preds_M <- JN_Magic_logo_M$null
ref_preds_M <- JN_Magic_logo_M$ref
pred_preds_M <- JN_Magic_logo_M$pred

# New variable
JN_Magic_obs_M <- JN_Magic_logo_M$out_data$Bites

# New variable (not sure what this would be in JN_Magic)
JN_Magic_total_M <- JN_Magic_logo_M$out_data$Bites

# 1 = whether you're doing the mean across rows or columns
# Trying to predict across patchm, to create something in a list. 
JN_Magic_null_M <- apply(null_preds_M,1,mean)
length(JN_Magic_null_M) #418
JN_Magic_ref_M <- apply(ref_preds_M,1,mean)
length(JN_Magic_ref_M) #418
JN_Magic_pred_M <- apply(pred_preds_M,1,mean)
length(JN_Magic_pred_M) #418

# Likelihood of observed data, given predicted data. We're looking for the lowest number here (this is a call to the probability distribution = how rampant a likely variable is. Given the distribution how likely is it that we observe one value conditional on the probability of being bitten). Remember, we are avoiding over fitting by leaving out data. 

# Mean absolute error, defined above. This is on the scale of the data, so the negative log likelihoods (which are a bit abstract) make more sense. 
mae(JN_Magic_null_M,JN_Magic_obs_M) #Run these for all columns of the posterior estimates of mae, and then apply the 95%CI to this). #1.019424
mae(JN_Magic_ref_M,JN_Magic_obs_M) #1.017725
mae(JN_Magic_pred_M, JN_Magic_obs_M) #1.017389

#######################CP

# In this code, we are creating subsets of the data
JN_Magic_levs_CP <- unique(JN_Magic_CP_use$Patch_ID)
JN_Magic_in_CP <- vector("list",length(JN_Magic_levs_CP))
JN_Magic_out_CP <- vector("list",length(JN_Magic_levs_CP))

# We are testing three different models:
# Model 1 is the observed chemistry
# Model 2 is the predicted chemistry
# Model 3 is a null model with no chemistry
ref_preds_CP <- vector("list",length(JN_Magic_levs_CP))
pred_preds_CP <- vector("list",length(JN_Magic_levs_CP))
null_preds_CP <- vector("list",length(JN_Magic_levs_CP))
#lists of predictions for each dataset

for(i in 1:length(JN_Magic_levs_CP)) #JN_Magic_levs is the unique number of patch ids
{
  # For each one of if (!requireNamespace("devtools", quietly = TRUE)){install.packages("devtools")}   devtools::install_github("jbisanz/qiime2R")the patch ids, this is looping through.
  # If you want to trouble shoot this, put i = 1 into the r consul and run line by line. 
  # Patch id out, running the model, and predicting on the left out patch
  
  # Data use to fit the model
  JN_Magic_in_CP[[i]] <- JN_Magic_CP_use[-which(JN_Magic_CP_use$Patch_ID==JN_Magic_levs_CP[i]),]
  
   # Data used to test the model
  JN_Magic_out_CP[[i]] <- JN_Magic_CP_use[which(JN_Magic_CP_use$Patch_ID==JN_Magic_levs_CP[i]),]
  
  m0_JN_Magic_CP <- stan_glmer(Bites_Binomial~Season+(1|Patch_ID),data=JN_Magic_in_CP[[i]],cores=4, family = "binomial", iter=10000)
  
  # Making predictions for the left out data
  null_preds_CP[[i]] <- posterior_epred(m0_JN_Magic_CP,newdata=JN_Magic_out_CP[[i]])
  
  mPRED_JN_Magic_CP <- stan_glmer(Bites_Binomial~Season+CP_Pred_std+(1|Patch_ID),data=JN_Magic_in_CP[[i]],cores=4, family = "binomial",iter=10000)
  
  pred_preds_CP[[i]] <- posterior_epred(mPRED_JN_Magic_CP,newdata=JN_Magic_out_CP[[i]])
  
  mREF_JN_Magic_CP <- stan_glmer(Bites_Binomial~Season+CP_Ref_std+(1|Patch_ID),data=JN_Magic_in_CP[[i]],cores=4, family = "binomial",iter=10000)
  
  ref_preds_CP[[i]] <- posterior_epred(mREF_JN_Magic_CP,newdata=JN_Magic_out_CP[[i]])
  }

null_preds_t_CP <- t(null_preds_CP)

# Extracting the predictions
# Binding the results together in a single data frame
JN_Magic_logo_CP <- vector("list",4)
names(JN_Magic_logo_CP) <- c("out_data","null","ref","pred")
JN_Magic_logo_CP[[1]] <- do.call("rbind",JN_Magic_out_CP)
JN_Magic_logo_CP[[2]] <- t(do.call("cbind",null_preds_CP))
JN_Magic_logo_CP[[3]] <- t(do.call("cbind",ref_preds_CP))
JN_Magic_logo_CP[[4]] <- t(do.call("cbind",pred_preds_CP))

# Save the object 
save(JN_Magic_logo_CP,file="JN_Magic_logo_CP.Rdata")

# Load(file="JN_Magic_logo.Rdata")
str(JN_Magic_logo_CP)

# Predicted data
# These are the predictions from the three models above. These are matrices, because we are doing this in a Bayesian context. 
null_preds_CP <- JN_Magic_logo_CP$null
ref_preds_CP <- JN_Magic_logo_CP$ref
pred_preds_CP <- JN_Magic_logo_CP$pred

# New variable
JN_Magic_obs_CP <- JN_Magic_logo_CP$out_data$Bites

# New variable (not sure what this would be in JN_Magic)
JN_Magic_total_CP <- JN_Magic_logo_CP$out_data$Bites

# 1 = whether you're doing the mean across rows or columns
# Trying to predict across patchm, to create something in a list. 
JN_Magic_null_CP <-apply(null_preds_CP,1,mean)
length(JN_Magic_null_CP) #426
JN_Magic_ref_CP <-apply(ref_preds_CP,1,mean)
length(JN_Magic_ref_CP) #426
JN_Magic_pred_CP <-apply(pred_preds_CP,1,mean)
length(JN_Magic_pred_CP) #426

# Likelihood of observed data, given predicted data. We're looking for the lowest number here (this is a call to the probability distribution = how rampant a likely variable is. Given the distribution how likely is it that we observe one value conditional on the probability of being bitten). Remember, we are avoiding over fitting by leaving out data. 

# Mean absolute error, defined above. This is on the scale of the data, so the negative log likelihoods (which are a bit abstract) make more sense. 
mae(JN_Magic_null_CP,JN_Magic_obs_CP) #Run these for all columns of the posterior estimates of mae, and then apply the 95%CI to this). #1.000369
mae(JN_Magic_ref_CP,JN_Magic_obs_CP) #1.017181
mae(JN_Magic_pred_CP, JN_Magic_obs_CP) #1.087752
```

# General posterior draw descriptive statistics

```{r}

nameo <- list.files()[-1]

chem_range <- read.csv("Text_Chemistry_Mins_Max_16Nov2025.csv")

load("mREF_JN_Magic_single_P.Rdata")
load("mPRED_JN_Magic_single_P.Rdata")
load("mREF_JN_Magic_single_M.Rdata")
load("mPRED_JN_Magic_single_M.Rdata")
load("mREF_JN_Magic_single_CP.Rdata")
load("mPRED_JN_Magic_single_CP.Rdata")

#All chemicals
chemm <- read.csv("Text_Chemistry_Mins_Max_16Nov2025.csv")

#First we will pull out the posterior draws:
#Phenolics
ref_JN_posteriors_P <- data.frame(mREF_JN_Magic_single_P)
pred_JN_posteriors_P <- data.frame(mPRED_JN_Magic_single_P)

#Monoterpenes
ref_JN_posteriors_M <- data.frame(mREF_JN_Magic_single_M)
pred_JN_posteriors_M <- data.frame(mPRED_JN_Magic_single_M)

#CP
ref_JN_posteriors_CP <- data.frame(mREF_JN_Magic_single_CP)
pred_JN_posteriors_CP <- data.frame(mPRED_JN_Magic_single_CP)

dim(ref_JN_posteriors_P) #20000    53
dim(pred_JN_posteriors_P) #20000    53
dim(ref_JN_posteriors_M) #20000    53
dim(pred_JN_posteriors_M) #20000    53
dim(ref_JN_posteriors_CP) #20000    53
dim(pred_JN_posteriors_CP) #20000    53

```

# Probability of Direction - Reference Chemistry

What is the percentage of draws that are either positive of negative?

```{r}
# Phenolics
length(which(ref_JN_posteriors_P$Phenolics_Ref_std>0))/length(ref_JN_posteriors_P$Phenolics_Ref_std) #0.89445
length(which(ref_JN_posteriors_P$Phenolics_Ref_std<0))/length(ref_JN_posteriors_P$Phenolics_Ref_std) #0.10555

# Monoterpenes
length(which(ref_JN_posteriors_M$Monoterpenes_Ref_std>0))/length(ref_JN_posteriors_M$Monoterpenes_Ref_std) #0.9777
length(which(ref_JN_posteriors_M$Monoterpenes_Ref_std<0))/length(ref_JN_posteriors_M$Monoterpenes_Ref_std) #0.0223

# Crude Proteins
length(which(ref_JN_posteriors_CP$CP_Ref_std>0))/length(ref_JN_posteriors_CP$CP_Ref_std) #1
length(which(ref_JN_posteriors_CP$CP_Ref_std<0))/length(ref_JN_posteriors_CP$CP_Ref_std) #0

```

# Probability of Direction - Predicted Chemistry

What is the percentage of draws that are either positive of negative?

```{r}

# Phenolics
length(which(pred_JN_posteriors_P$Phenolics_Pred_std>0))/length(pred_JN_posteriors_P$Phenolics_Pred_std) #0.9381
length(which(pred_JN_posteriors_P$Phenolics_Pred_std<0))/length(pred_JN_posteriors_P$Phenolics_Pred_std) #0.06305

# Monoterpenes
length(which(pred_JN_posteriors_M$Monoterpenes_Pred_std>0))/length(pred_JN_posteriors_M$Monoterpenes_Pred_std) #0.96275
length(which(pred_JN_posteriors_M$Monoterpenes_Pred_std<0))/length(pred_JN_posteriors_M$Monoterpenes_Pred_std) #0.03725

# Crude Proteins
length(which(pred_JN_posteriors_CP$CP_Pred_std>0))/length(pred_JN_posteriors_CP$CP_Pred_std) #1
length(which(pred_JN_posteriors_CP$CP_Pred_std<0))/length(pred_JN_posteriors_CP$CP_Pred_std) #0

```

# Effect Size Min & Max - Reference chemistry

```{r}

# Referencing min and max from data frame
chemm$Ref_Min[which(chemm$Site=="JN_Magic" & chemm$Chemical=="Crude Protein")] 
chemm$Ref_Max[which(chemm$Site=="JN_Magic" & chemm$Chemical=="Crude Protein")] 

# Setting up an empty vector to fill in with predictions
predicted_diff_cp_ref <- rep(NA,times=ncol(ref_JN_posteriors_CP))
predicted_diff_Monoterpenes_ref <- rep(NA,times=ncol(ref_JN_posteriors_M))
predicted_diff_Phenolics_ref <- rep(NA,times=ncol(ref_JN_posteriors_P))

# Phenolics
for(i in 1:ncol(ref_JN_posteriors_P)){

# This is just an intercept + slope*x. exp ensures it is a probability. We are looping over every value of the posterior draw to propagate uncertainty.
min_pred_P <- exp(ref_JN_posteriors_P$X.Intercept.[i]+ref_JN_posteriors_P$Phenolics_Ref_std[i]*chemm$Ref_Min[which(chemm$Site=="JN_Magic" & chemm$Chemical=="Phenolics")])
  
max_pred_P <- exp(ref_JN_posteriors_P$X.Intercept.[i]+ref_JN_posteriors_P$Phenolics_Ref_std[i]*chemm$Ref_Max[which(chemm$Site=="JN_Magic" & chemm$Chemical=="Phenolics")])
  
predicted_diff_Phenolics_ref[i] <- max_pred_P-min_pred_P # This is the difference we will store. feel free to reverse the order here, depending on what you want to report.
}  

quantile(predicted_diff_Phenolics_ref,c(0.025,0.5,0.975))
#       2.5%         50%       97.5% 
#-0.01835510  0.08762001  1.12895019 


# Monoterpenes
for(i in 1:ncol(ref_JN_posteriors_M)){

# This is just an intercept + slope*x. plogis ensures it is a probability. We are looping over every value of the posterior draw to propagate uncertainty.
min_pred_M <- plogis(ref_JN_posteriors_M$X.Intercept.[i]+ref_JN_posteriors_M$Monoterpenes_Ref_std[i]*chemm$Ref_Min[which(chemm$Site=="JN_Magic" & chemm$Chemical=="Monoterpenes")])
  
max_pred_M <- plogis(ref_JN_posteriors_M$X.Intercept.[i]+ref_JN_posteriors_M$Monoterpenes_Ref_std[i]*chemm$Ref_Max[which(chemm$Site=="JN_Magic" & chemm$Chemical=="Monoterpenes")])
  
predicted_diff_Monoterpenes_ref[i] <- max_pred_M-min_pred_M # This is the difference we will store.
}  

quantile(predicted_diff_Monoterpenes_ref,c(0.025,0.5,0.975)) 
#       2.5%          50%        97.5% 
#0.004518973 0.100605431 0.339281279

# CP

for(i in 1:ncol(ref_JN_posteriors_CP)){

# This is just an intercept + slope*x. plogis ensures it is a probability. We are looping over every value of the posterior draw to propagate uncertainty.
min_pred_CP <- plogis(ref_JN_posteriors_CP$X.Intercept.[i]+ref_JN_posteriors_CP$CP_Ref_std[i]*chemm$Ref_Min[which(chemm$Site=="JN_Magic" & chemm$Chemical=="Crude Protein")])
  
max_pred_CP <- plogis(ref_JN_posteriors_CP$X.Intercept.[i]+ref_JN_posteriors_CP$CP_Ref_std[i]*chemm$Ref_Max[which(chemm$Site=="JN_Magic" & chemm$Chemical=="Crude Protein")])
  
predicted_diff_cp_ref[i] <- max_pred_CP-min_pred_CP # This is the difference we will store. 
  }  

quantile(predicted_diff_cp_ref,c(0.025,0.5,0.975)) 

#      2.5%        50%      97.5% 
#0.02837297 0.18236810 0.57020162 


```

# Effect Size Min & Max - Predicted Chemistry

```{r}

# Referencing min and max from data frame
chemm$Pred_Min[which(chemm$Site=="JN_Magic" & chemm$Chemical=="Crude Protein")] 
chemm$Pred_Max[which(chemm$Site=="JN_Magic" & chemm$Chemical=="Crude Protein")] 

# Setting up an empty vector to fill in with predictions
predicted_diff_Phenolics_pred <- rep(NA,times=ncol(pred_JN_posteriors_P))
predicted_diff_Monoterpenes_pred <- rep(NA,times=ncol(pred_JN_posteriors_M))
predicted_diff_cp_pred <- rep(NA,times=ncol(pred_JN_posteriors_CP))

# Phenolics
for(i in 1:ncol(pred_JN_posteriors_P)){

# This is just an intercept + slope*x. plogis ensures it is a probability. We are looping over every value of the posterior draw to propagate uncertainty.
min_pred_P <- plogis(pred_JN_posteriors_P$X.Intercept.[i]+pred_JN_posteriors_P$Phenolics_Pred_std[i]*chemm$Pred_Min[which(chemm$Site=="JN_Magic" & chemm$Chemical=="Phenolics")])
  
max_pred_P <- plogis(pred_JN_posteriors_P$X.Intercept.[i]+pred_JN_posteriors_P$Phenolics_Pred_std[i]*chemm$Pred_Max[which(chemm$Site=="JN_Magic" & chemm$Chemical=="Phenolics")])
  
predicted_diff_Phenolics_pred[i] <- max_pred_P-min_pred_P # This is the difference we will store. 
}  

quantile(predicted_diff_Phenolics_pred,c(0.025,0.5,0.975)) 
#        2.5%          50%        97.5% 
#-0.02559411  0.04017733  0.16882918 

# Monoterpenes
for(i in 1:ncol(pred_JN_posteriors_M)){

# This is just an intercept + slope*x. plogis ensures it is a probability. We are looping over every value of the posterior draw to propagate uncertainty.
min_pred_M <- plogis(pred_JN_posteriors_M$X.Intercept.[i]+pred_JN_posteriors_M$Monoterpenes_Pred_std[i]*chemm$Pred_Min[which(chemm$Site=="JN_Magic" & chemm$Chemical=="Monoterpenes")])
  
max_pred_M <- plogis(pred_JN_posteriors_M$X.Intercept.[i]+pred_JN_posteriors_M$Monoterpenes_Pred_std[i]*chemm$Pred_Max[which(chemm$Site=="JN_Magic" & chemm$Chemical=="Monoterpenes")])
  
predicted_diff_Monoterpenes_pred[i] <- max_pred_M-min_pred_M # This is the difference we will store. 
}  

quantile(predicted_diff_Monoterpenes_pred,c(0.025,0.5,0.975)) 
#      2.5%        50%      97.5% 
#-0.009440813  0.035605060  0.094180903 

# CP
for(i in 1:ncol(pred_JN_posteriors_CP)){

# This is just an intercept + slope*x. plogis ensures it is a probability. We are looping over every value of the posterior draw to propagate uncertainty.
min_pred_CP <- plogis(pred_JN_posteriors_CP$X.Intercept.[i]+pred_JN_posteriors_CP$CP_Pred_std[i]*chemm$Pred_Min[which(chemm$Site=="JN_Magic" & chemm$Chemical=="Crude Protein")])
  
max_pred_CP <- plogis(pred_JN_posteriors_CP$X.Intercept.[i]+pred_JN_posteriors_CP$CP_Pred_std[i]*chemm$Pred_Max[which(chemm$Site=="JN_Magic" & chemm$Chemical=="Crude Protein")])
  
predicted_diff_cp_pred[i] <- max_pred_CP-min_pred_CP # This is the difference we will store.
  }  

quantile(predicted_diff_cp_pred,c(0.025,0.5,0.975)) 
#     2.5%       50%     97.5% 
#0.1201562 0.3433512 0.6886870 

```
