---
title: "Chapter 2 - Bite Data - Chemistry - Predicted Chemistry at KG Magic Site"
output:
  pdf_document: default
  html_document: default
---

This R Markdown file will input data for the KG Magic (Magic = Camas Prairie) site and prepare it for three downstream analyses determining the effects of chemistry and predicted chemistry on bite data. Negative binomial distribution (check this). 

KG Magic is a pygmy rabbit site that sampled active mounds only - paired on (3x3 grid=9) and off mound (3x4 cardinal directions=12). Individual plant data is available for this site. Data was collected in Spring and Winter, and had no upper limit for the number of bites counted. A negative binomial distribution was used to analyze this data set.

In addition to these data, individual pellet counts within a meter of each individual shrub. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#Load libraries
library("rprojroot")
library("loo")
library("rstanarm")
options(mc.cores = parallel::detectCores())
library("ggplot2")
library("bayesplot")
theme_set(bayesplot::theme_default(base_family = "sans"))
library("MASS")
library("lme4")
library("brms")
library("rstanarm")
```

# Functions

These functions are used throughout the markdown, and include ways for evaluating predictive error and standardizing the inputs. 

## Root mean square error (RSME)
This shows the difference between an estimator and the values observed, and provides a measure of accuracy.

## Mean absolute error (MAE)
This is a measure of errors between paired observations expressing the same phenomenon, and is one of a number of ways of comparing forecasts with their eventual outcomes.

## Residual sum of squares (RSS)
This is a measure of discrepancy between the data (x) and the model (d). A small value indicates a good fit between the data and the model (0 is a perfect fit). This number can be infinite, as far as I'm aware.

## Total sum of squares (TSS)

This is the explained sum of squares plus the RSS. 

## R2

The proportion of variance explained by the model out of the total variance in the data (0-1). Closer to one means 100% fit. 

## splt

Tidies up the data by removing the double names

## stdize

Putting all of the covariates on the same scale 
http://www.stat.columbia.edu/~gelman/research/published/standardizing7.pdf


```{r}
# This first function is for root mean square, where m is the model predictions, and x is the data.
rmse <- function(m,x) 
{
  sqrt(mean((x-m)^2,na.rm=T))
}

# This function is for mean absolute error, where m is the model predictions, and x is the data. 
mae <- function(m,x)
{
  mean(abs(((x-m))),na.rm=T)
}

# This function is for residual sum of squares
RSS <- function(m,x) 
{
  sum((((m))-(x))^2)
}

# This function is for total sum of squares
TSS <- function(x) 
{
  sum(((x)-(mean(x)))^2)
  }

R2<-function(m,x,logo=F) {
  mors<-na.omit(data.frame(m,x))
  m<-mors$m
  x<-mors$x
  
  if(logo==F) {return(1-RSS(m,x)/TSS(x))} else {return(1-RSS1(m,x)/TSS1(x))}
}

# Split names
splt=function(x,split,num) {
  
  x<-as.character(x)
  p1=strsplit(x,split=split,fixed=T)
  p2=unlist(lapply(p1,"[",num))
  return(p2)
}

# Standardize covariates
stdize<-function(x) {(x-mean(x,na.rm=T))/(2*sd(x,na.rm=T))}

```

# Read in Files

In the input file for the KG Magic site, you'll see that the number of bites are taken from individual plants (as opposed to averaged across morphotypes).  

```{r}
# Main data set that includes all the sites, chemotype levels. We're setting periods and blank spaces to read in to R as NA:
Phenolics <- read.csv("Phenolics.csv", na.strings=c("."," ","","NA"))
Monoterpenes <- read.csv("Monoterpenes.csv", na.strings=c("."," ","","NA"))
Crude_Protein <- read.csv("Crude_protein.csv", na.strings=c("."," ","","NA"))

# Subset datasets to KG Magic site:
KG_Magic_P <-subset(Phenolics,Phenolics$Site=="KGMagic") 
KG_Magic_M <-subset(Monoterpenes, Monoterpenes$Site=="KGMagic") 
KG_Magic_CP <-subset(Crude_Protein,Crude_Protein$Site=="KGMagic") 

# See the distribution of number of bites. You'll see there is no averaged data here. 
unique(KG_Magic_P$Bites)
unique(KG_Magic_M$Bites)
unique(KG_Magic_CP$Bites)

## Check out the dimensions of the input data:
# Bites
length(KG_Magic_P$Bites) #428
table(KG_Magic_P$Bites)

length(KG_Magic_M$Bites) #498 
table(KG_Magic_M$Bites)

length(KG_Magic_CP$Bites) #499
table(KG_Magic_CP$Bites)

# Season
table(KG_Magic_P$Season) #Spring = 350, Winter = 78
table(KG_Magic_M$Season) #Spring = 404, Winter = 94
table(KG_Magic_CP$Season) #Spring = 405, Winter = 94

# Species
table(KG_Magic_P$Species) #3-tip = 8, Dwarf = 2, Wyoming = 418
table(KG_Magic_M$Species) #3-tip = 8, Dwarf = 5, Wyoming = 485
table(KG_Magic_CP$Species) #3-tip = 8, Dwarf = 5, Wyoming = 486

# Plant height # Not available at this site
table(KG_Magic_P$PlantSize) #table of extent 0
table(KG_Magic_M$PlantSize) #table of extent 0
table(KG_Magic_CP$PlantSize) #table of extent 0

# Patch type
table(KG_Magic_P$PatchType) #Off = 244, On = 184
table(KG_Magic_M$PatchType) #Off = 282, On = 216
table(KG_Magic_CP$PatchType) #Off = 283, On = 216

#Patch_ID here is the random effect # Double check this
table(KG_Magic_P$Patch_ID)[-which(table(KG_Magic_P$Patch_ID)==0)] #named integer(0)
table(KG_Magic_M$Patch_ID)[-which(table(KG_Magic_P$Patch_ID)==0)] #named integer(0)
table(KG_Magic_CP$Patch_ID)[-which(table(KG_Magic_P$Patch_ID)==0)] #named integer(0)

# Standardize our covariates
# Putting all of the covariates on the same scale 
# http://www.stat.columbia.edu/~gelman/research/published/standardizing7.pdf
stdize<-function(x) {(x-mean(x,na.rm=T))/(2*sd(x,na.rm=T))}

KG_Magic_P$Phenolics_Pred_std <- stdize(KG_Magic_P$Phenolics_newpred)
KG_Magic_M$Monoterpenes_Pred_std <- stdize(KG_Magic_M$Monoterpenes_newpred)
KG_Magic_CP$CP_Pred_std<-stdize(KG_Magic_CP$CP_newpred)

KG_Magic_P$Phenolics_Ref_std <- stdize(KG_Magic_P$Phenolics_Ref)
KG_Magic_M$Monoterpenes_Ref_std<-stdize(KG_Magic_M$Monoterpenes_Ref)
KG_Magic_CP$CP_Ref_std<-stdize(KG_Magic_CP$CP_Ref)

# Create the data set that we use moving forward
KG_Magic_P_use <- na.omit(data.frame(Bites=KG_Magic_P$Bites, PatchType=KG_Magic_P$PatchType, Season=KG_Magic_P$Season, Phenolics_Pred_std=KG_Magic_P$Phenolics_Pred_std,Patch_ID=KG_Magic_P$Patch_ID,Phenolics_Ref_std=KG_Magic_P$Phenolics_Ref_std))

KG_Magic_M_use <- na.omit(data.frame(Bites=KG_Magic_M$Bites,PatchType=KG_Magic_M$PatchType, Season=KG_Magic_M$Season,Monoterpenes_Pred_std=KG_Magic_M$Monoterpenes_Pred_std,Patch_ID=KG_Magic_M$Patch_ID,Monoterpenes_Ref_std=KG_Magic_M$Monoterpenes_Ref_std))

KG_Magic_CP_use <- na.omit(data.frame(Bites=KG_Magic_CP$Bites, CP_Pred_std=KG_Magic_CP$CP_Pred_std,PatchType=KG_Magic_CP$PatchType, Season=KG_Magic_CP$Season,Patch_ID=KG_Magic_CP$Patch_ID,CP_Ref_std=KG_Magic_CP$CP_Ref_std))

## Check out the dimensions of the final data. Remember, NAs have been removed:
# Bites
length(KG_Magic_P_use$Bites) #428
table(KG_Magic_P_use$Bites)

length(KG_Magic_M_use$Bites) #486
table(KG_Magic_M_use$Bites)

length(KG_Magic_CP_use$Bites) #487
table(KG_Magic_CP_use$Bites) 

# Season
table(KG_Magic_P_use$Season) #Spring = 350, winter = 78
table(KG_Magic_M_use$Season) #Spring = 404, winter = 82
table(KG_Magic_CP_use$Season) #Spring = 405, winter = 82

# Patch type
table(KG_Magic_P_use$PatchType) #Off = 244, on = 184
table(KG_Magic_M_use$PatchType) #Off = 277, on = 209
table(KG_Magic_CP_use$PatchType) #Off = 278, on = 209

#Mins and Maxes
min(KG_Magic_P_use$Phenolics_Ref_std) #-1.238274
max(KG_Magic_P_use$Phenolics_Ref_std) #3.270009
min(KG_Magic_P_use$Phenolics_Pred_std) #-1.363222
max(KG_Magic_P_use$Phenolics_Pred_std) #1.415847

min(KG_Magic_M_use$Monoterpenes_Ref_std) #-0.9916437
max(KG_Magic_M_use$Monoterpenes_Ref_std) #1.501891
min(KG_Magic_M_use$Monoterpenes_Pred_std) #-1.459817
max(KG_Magic_M_use$Monoterpenes_Pred_std) #0.8884188

min(KG_Magic_CP_use$CP_Ref_std) #-1.30037
max(KG_Magic_CP_use$CP_Ref_std) #2.488451
min(KG_Magic_CP_use$CP_Pred_std) #-1.34902
max(KG_Magic_CP_use$CP_Pred_std) #2.00042

## Descriptive Stats

# Phenolics
mean(KG_Magic_P$Phenolics_Ref, na.rm=TRUE) #11.94784
sd(KG_Magic_P$Phenolics_Ref, na.rm=TRUE) #4.441225
mean(KG_Magic_P$Phenolics_newpred, na.rm=TRUE) #11.9506
sd(KG_Magic_P$Phenolics_newpred, na.rm=TRUE) #5.961768

mean(KG_Magic_P_use$Phenolics_Ref_std, na.rm=TRUE) #5.162018e-17
sd(KG_Magic_P_use$Phenolics_Ref_std, na.rm=TRUE) #0.5
mean(KG_Magic_P_use$Phenolics_Pred_std, na.rm=TRUE) #-2.879317e-17
sd(KG_Magic_P_use$Phenolics_Pred_std, na.rm=TRUE) #0.5

# Monoterpenes
mean(KG_Magic_M$Monoterpenes_Ref, na.rm=TRUE) #2204.957
sd(KG_Magic_M$Monoterpenes_Ref, na.rm=TRUE) #893.7906
mean(KG_Magic_M$Monoterpenes_newpred, na.rm=TRUE) #2176.32
sd(KG_Magic_M$Monoterpenes_newpred, na.rm=TRUE) #722.4094

mean(KG_Magic_M_use$Monoterpenes_Ref_std, na.rm=TRUE) #0.01686997
sd(KG_Magic_M_use$Monoterpenes_Ref_std, na.rm=TRUE) #0.4939539
mean(KG_Magic_M_use$Monoterpenes_Pred_std, na.rm=TRUE) #0.01791427
sd(KG_Magic_M_use$Monoterpenes_Pred_std, na.rm=TRUE) #0.4920768

# Crude Proteins
mean(KG_Magic_CP$CP_Ref, na.rm=TRUE) #10.47658
sd(KG_Magic_CP$CP_Ref, na.rm=TRUE) #1.913524
mean(KG_Magic_CP$CP_newpred, na.rm=TRUE) #10.49879
sd(KG_Magic_CP$CP_newpred, na.rm=TRUE) #1.537988

mean(KG_Magic_CP_use$CP_Ref_std, na.rm=TRUE) #0.009071084
sd(KG_Magic_CP_use$CP_Ref_std, na.rm=TRUE) #0.5018873
mean(KG_Magic_CP_use$CP_Pred_std, na.rm=TRUE) #0.003424819
sd(KG_Magic_CP_use$CP_Pred_std, na.rm=TRUE) #0.5024934

```

# Question 1: What are the effects of chemistry on bites?

```{r}
#.nb = negative binomial

mREF_KG_Magic_single_P<-rstanarm::stan_glmer.nb(Bites~Season+Phenolics_Ref_std+(1|Patch_ID),data=KG_Magic_P_use,cores=4, iter=10000)

mREF_KG_Magic_single_M<-rstanarm::stan_glmer.nb(Bites~Season+Monoterpenes_Ref_std+(1|Patch_ID),data=KG_Magic_M_use,cores=4, iter=10000)

mREF_KG_Magic_single_CP<-rstanarm::stan_glmer.nb(Bites~Season+CP_Ref_std+(1|Patch_ID),data=KG_Magic_CP_use,cores=4, iter=10000)

summary(mREF_KG_Magic_single_P)
summary(mREF_KG_Magic_single_M)
summary(mREF_KG_Magic_single_CP)

png(file="./KG_Magic_Reference_P.png")
plot(mREF_KG_Magic_single_P,regex_pars="_std")
dev.off()
save(mREF_KG_Magic_single_P, file = "mREF_KG_Magic_single_P.Rdata")

png(file="./KG_Magic_Reference_M.png")
plot(mREF_KG_Magic_single_M,regex_pars="_std")
dev.off()
save(mREF_KG_Magic_single_M, file = "mREF_KG_Magic_single_M.Rdata")

png(file="./KG_Magic_Reference_CP.png")
plot(mREF_KG_Magic_single_CP,regex_pars="_std")
dev.off()
save(mREF_KG_Magic_single_CP, file = "mREF_KG_Magic_single_CP.Rdata")

##############
# Extract posteriors

KG_Magic_single_REF_P <- as.data.frame(mREF_KG_Magic_single_P)
KG_Magic_single_REF_M <- as.data.frame(mREF_KG_Magic_single_M)
KG_Magic_single_REF_CP <- as.data.frame(mREF_KG_Magic_single_CP)

Phenolics_out <- KG_Magic_single_REF_P$Phenolics_Ref_std
Phenolics_REF_cat <- rep("Phenolics_REF",times=length(Phenolics_out))

CP_out <- KG_Magic_single_REF_CP$CP_Ref_std
CP_REF_cat <- rep("CP_REF",times=length(CP_out))

Monoterpenes_out <- KG_Magic_single_REF_M$Monoterpenes_Ref_std
Monoterpenes_REF_cat <- rep("Monoterpenes_REF",times=length(Monoterpenes_out))

pos_draws <- c(Phenolics_out,CP_out,Monoterpenes_out)

chem_type <- c(Phenolics_REF_cat,CP_REF_cat,Monoterpenes_REF_cat)

KG_Magic_single_REF <- data.frame(pos_draws,chem_type)

KG_Magic_single_REF$Site<-rep("KG_Magic",times=nrow(KG_Magic_single_REF))

save(KG_Magic_single_REF ,file="KG_Magic_single_REF.Rdata")

```

# Question 2: Does inference on chemistry effects change when using predicted, rather than observed values?

```{r}

mPRED_KG_Magic_single_P <-rstanarm::stan_glmer.nb(Bites~Season+Phenolics_Pred_std+(1|Patch_ID),data=KG_Magic_P_use,cores=4,iter=10000)

mPRED_KG_Magic_single_M <-rstanarm::stan_glmer.nb(Bites~Season+Monoterpenes_Pred_std+(1|Patch_ID),data=KG_Magic_M_use,cores=4,iter=10000)

mPRED_KG_Magic_single_CP <-rstanarm::stan_glmer.nb(Bites~Season+CP_Pred_std+(1|Patch_ID),data=KG_Magic_CP_use,cores=4,iter=10000)

summary(mPRED_KG_Magic_single_P)
summary(mPRED_KG_Magic_single_M)
summary(mPRED_KG_Magic_single_CP)

png(file="./KG_Magic_Predicted_P.png")
plot(mPRED_KG_Magic_single_P,regex_pars="_std")
dev.off()
save(mPRED_KG_Magic_single_P, file = "mPRED_KG_Magic_single_P.Rdata")

png(file="./KG_Magic_Predicted_M.png")
plot(mPRED_KG_Magic_single_M,regex_pars="_std")
dev.off()
save(mPRED_KG_Magic_single_M, file = "mPRED_KG_Magic_single_M.Rdata")

png(file="./KG_Magic_Predicted_CP.png")
plot(mPRED_KG_Magic_single_CP,regex_pars="_std")
dev.off()
save(mPRED_KG_Magic_single_CP, file = "mPRED_KG_Magic_single_CP.Rdata")

##############
# Extract posteriors

KG_Magic_single_PRED_P <- as.data.frame(mPRED_KG_Magic_single_P)
KG_Magic_single_PRED_M <- as.data.frame(mPRED_KG_Magic_single_M)
KG_Magic_single_PRED_CP <- as.data.frame(mPRED_KG_Magic_single_CP)

Phenolics_out <- KG_Magic_single_PRED_P$Phenolics_Pred_std
Phenolics_PRED_cat <- rep("Phenolics_PRED",times=length(Phenolics_out))

CP_out <- KG_Magic_single_PRED_CP$CP_Pred_std
CP_PRED_cat <- rep("CP_PRED",times=length(CP_out))

Monoterpenes_out <- KG_Magic_single_PRED_M$Monoterpenes_Pred_std
Monoterpenes_PRED_cat <- rep("Monoterpenes_PRED",times=length(Monoterpenes_out))

pos_draws <- c(Phenolics_out,CP_out,Monoterpenes_out)

chem_type <- c(Phenolics_PRED_cat,CP_PRED_cat,Monoterpenes_PRED_cat)

KG_Magic_single_PRED <- data.frame(pos_draws,chem_type)

KG_Magic_single_PRED$Site<-rep("KG_Magic",times=nrow(KG_Magic_single_PRED))

save(KG_Magic_single_PRED ,file="KG_Magic_single_PRED.Rdata")

```

# Question 3: how does the predictions changes when using obs vs predicted chemistry?

# https://onlinelibrary.wiley.com/doi/full/10.1111/ecog.02881
#paper that describes our leave-one-out approach

```{r}
########################Phenolics
# In this code, we are creating subsets of the data
KG_levs_P <- unique(KG_Magic_P_use$Patch_ID)
KG_in_P <- vector("list",length(KG_levs_P))
KG_out_P <- vector("list",length(KG_levs_P))

# We are testing three different models:
# Model 1 is the observed chemistry
# Model 2 is the predicted chemistry
# Model 3 is a null model with no chemistry
ref_preds_P <- vector("list",length(KG_levs_P))
pred_preds_P <- vector("list",length(KG_levs_P))
null_preds_P <- vector("list",length(KG_levs_P))
# Lists of predictions for each dataset

ref_k_P <- vector("list",length(KG_levs_P))
pred_k_P <- vector("list",length(KG_levs_P))
null_k_P<- vector("list",length(KG_levs_P))

for(i in 1:length(KG_levs_P)) #KG_levs is the unique number of patch ids
{
  # For each one of if (!requireNamespace("devtools", quietly = TRUE)){install.packages("devtools")}   devtools::install_github("jbisanz/qiime2R")the patch ids, this is looping through.
  # If you want to trouble shoot this, put i = 1 into the r console and run line by line.
  # Patch id out, running the model, and predicting on the left out patch
 
  # Data use to fit the model
  KG_in_P[[i]] <- KG_Magic_P_use[-which(KG_Magic_P_use$Patch_ID==KG_levs_P[i]),]
 
  # Data used to test the model
  KG_out_P[[i]] <- KG_Magic_P_use[which(KG_Magic_P_use$Patch_ID==KG_levs_P[i]),]
 
  M0_KG_Magic_P <- stan_glmer.nb(Bites~Season+(1|Patch_ID),data=KG_in_P[[i]],cores=4, iter=10000)
 
  # Making predictions for the left out data
  null_preds_P[[i]] <- posterior_predict(M0_KG_Magic_P,newdata=KG_out_P[[i]])
  null_k_P[[i]] <- data.frame(M0_KG_Magic_P)$reciprocal_dispersion
 
 
  mPRED_KG_Magic_P <- stan_glmer.nb(Bites~Season+Phenolics_Pred_std+(1|Patch_ID),data=KG_in_P[[i]],cores=4, iter=10000)
 
  pred_preds_P[[i]] <- posterior_predict(mPRED_KG_Magic_P,newdata=KG_out_P[[i]])
  pred_k_P[[i]] <- data.frame(mPRED_KG_Magic_P)$reciprocal_dispersion
 
  mREF_KG_Magic_P <- stan_glmer.nb(Bites~Season+Phenolics_Ref_std+(1|Patch_ID),data=KG_in_P[[i]],cores=4)
 
  ref_preds_P[[i]] <- posterior_predict(mPRED_KG_Magic_P,newdata=KG_out_P[[i]])
  ref_k_P[[i]] <- data.frame(mREF_KG_Magic_P)$reciprocal_dispersion
  }

# Extracting the predictions
# Binding the results together in a single data frame
KG_logo_P<-vector("list",4)
names(KG_logo_P)<-c("out_data","null","ref","pred")
KG_logo_P[[1]]<-do.call("rbind",KG_out_P)
KG_logo_P[[2]]<-t(do.call("cbind",null_preds_P))
KG_logo_P[[3]]<-t(do.call("cbind",ref_preds_P))
KG_logo_P[[4]]<-t(do.call("cbind",pred_preds_P))

KG_k_p <- vector("list",4)
names(KG_k_p)<-c("out_data","null","ref","pred")

KG_k_p[[1]]<-do.call("rbind",KG_out_P)
KG_k_p[[2]]<-t(do.call("cbind",null_k_P))
KG_k_p[[3]]<-t(do.call("cbind",ref_k_P))
KG_k_p[[4]]<-t(do.call("cbind",pred_k_P))

# Save the object
save(KG_k_p,file="KG_k_P.Rdata")

# Load(file="KG_logo_P.Rdata")
str(KG_logo_P)

# Predicted data
# These are the predictions from the three models above. These are matrices, because we are doing this in a Bayesian context. 
null_preds_P <- KG_logo_P$null

ref_preds_P <- KG_logo_P$ref

pred_preds_P <- KG_logo_P$pred

# New variable
KG_obs_P <- KG_logo_P$out_data$Bites

# New variable (not sure what this would be in KG_Magic)
KG_total_P <- KG_logo_P$out_data$Bites

# 1 = whether you're doing the mean across rows or columns
# Trying to predict across patchm, to create something in a list. 
KG_null_P<-apply(null_preds_P,1,mean)
length(KG_null_P)
KG_ref_P<-apply(ref_preds_P,1,mean)
length(KG_ref_P)
KG_pred_P<-apply(pred_preds_P,1,mean)
length(KG_pred_P)

# Likelihood of observed data, given predicted data. 

# Mean absolute error, defined above. This is on the scale of the data, so the negative log likelihoods (which are a bit abstract) make more sense. 
mae(KG_null_P,KG_obs_P) #9.747313
mae(KG_ref_P,KG_obs_P) #9.881806
mae(KG_pred_P, KG_obs_P) #9.876057

###########################Monoterpenes
# In this code, we are creating subsets of the data
KG_levs_M <- unique(KG_Magic_M_use$Patch_ID)
KG_in_M <- vector("list",length(KG_levs_M))
KG_out_M <- vector("list",length(KG_levs_M))

# We are testing three different models:
# Model 1 is the observed chemistry
# Model 2 is the predicted chemistry
# Model 3 is a null model with no chemistry
ref_preds_M <- vector("list",length(KG_levs_M))
pred_preds_M <- vector("list",length(KG_levs_M))
null_preds_M <- vector("list",length(KG_levs_M))
# Lists of predictions for each dataset

ref_k_M <-vector("list",length(KG_levs_M))
pred_k_M <-vector("list",length(KG_levs_M))
null_k_M <-vector("list",length(KG_levs_M))

for(i in 1:length(KG_levs_M)) #KG_levs is the unique number of patch ids
{
  # For each one of if (!requireNamespace("devtools", quietly = TRUE)){install.packages("devtools")}   devtools::install_github("jbisanz/qiime2R")the patch ids, this is looping through.
  # If you want to trouble shoot this, put i = 1 into the r console and run line by line.
  # Patch id out, running the model, and predicting on the left out patch
 
  # Data use to fit the model
  KG_in_M[[i]] <- KG_Magic_M_use[-which(KG_Magic_M_use$Patch_ID==KG_levs_M[i]),]
 
  # Data used to test the model
  KG_out_M[[i]] <- KG_Magic_M_use[which(KG_Magic_M_use$Patch_ID==KG_levs_M[i]),]
 
  M0_KG_Magic_M <- stan_glmer.nb(Bites~Season+(1|Patch_ID),data=KG_in_M[[i]],cores=4, iter=10000)
 
  # Making predictions for the left out data
  null_preds_M[[i]] <- posterior_predict(M0_KG_Magic_M,newdata=KG_out_M[[i]])
  null_k_M[[i]] <- data.frame(M0_KG_Magic_M)$reciprocal_dispersion
 
 
  mPRED_KG_Magic_M <- stan_glmer.nb(Bites~Season+Monoterpenes_Pred_std+(1|Patch_ID),data=KG_in_M[[i]],cores=4, iter=10000)
 
  pred_preds_M[[i]] <- posterior_predict(mPRED_KG_Magic_M,newdata=KG_out_M[[i]])
  pred_k_M[[i]] <- data.frame(mPRED_KG_Magic_M)$reciprocal_dispersion
 
  mREF_KG_Magic_M <- stan_glmer.nb(Bites~Season+Monoterpenes_Ref_std+(1|Patch_ID),data=KG_in_M[[i]],cores=4)
 
  ref_preds_M[[i]] <- posterior_predict(mPRED_KG_Magic_M,newdata=KG_out_M[[i]])
  ref_k_M[[i]] <- data.frame(mREF_KG_Magic_M)$reciprocal_dispersion
  }

# Extracting the predictions
# Binding the results together in a single data frame
KG_logo_M<-vector("list",4)
names(KG_logo_M)<-c("out_data","null","ref","pred")
KG_logo_M[[1]] <- do.call("rbind",KG_out_M)
KG_logo_M[[2]] <- t(do.call("cbind",null_preds_M))
KG_logo_M[[3]] <- t(do.call("cbind",ref_preds_M))
KG_logo_M[[4]] <- t(do.call("cbind",pred_preds_M))

KG_k_M <- vector("list",4)
names(KG_k_M) <- c("out_data","null","ref","pred")

KG_k_M[[1]] <- do.call("rbind",KG_out_M)
KG_k_M[[2]] <- t(do.call("cbind",null_k_M))
KG_k_M[[3]] <- t(do.call("cbind",ref_k_M))
KG_k_M[[4]] <- t(do.call("cbind",pred_k_M))

# Save the object
save(KG_k_M,file="KG_k_M.Rdata")

# Load(file="KG_logo_M.Rdata")
str(KG_logo_M)

# Predicted data
# These are the predictions from the three models above. These are matrices, because we are doing this in a Bayesian context. 
null_preds_M <- KG_logo_M$null
ref_preds_M <- KG_logo_M$ref
pred_preds_M <- KG_logo_M$pred

# New variable
KG_obs_M <- KG_logo_M$out_data$Bites

# New variable (not sure what this would be in KG_Magic)
KG_total_M <- KG_logo_M$out_data$Bites

# 1 = whether you're doing the mean across rows or columns
# Trying to predict across patchm, to create something in a list. 
KG_null_M <- apply(null_preds_M,1,mean)
length(KG_null_M) #486
KG_ref_M <- apply(ref_preds_M,1,mean)
length(KG_ref_M) #486
KG_pred_M <- apply(pred_preds_M,1,mean)
length(KG_pred_M) #486

# Likelihood of observed data, given predicted data. 

# Mean absolute error, defined above. This is on the scale of the data, so the negative log likelihoods (which are a bit abstract) make more sense. 
mae(KG_null_M,KG_obs_M) #9.882156
mae(KG_ref_M,KG_obs_M) #9.925131
mae(KG_pred_M, KG_obs_M) #9.914694

###########################Crude Protein
# In this code, we are creating subsets of the data
KG_levs_CP <- unique(KG_Magic_CP_use$Patch_ID)
KG_in_CP <- vector("list",length(KG_levs_CP))
KG_out_CP <- vector("list",length(KG_levs_CP))

# We are testing three different models:
# Model 1 is the observed chemistry
# Model 2 is the predicted chemistry
# Model 3 is a null model with no chemistry
ref_preds_CP <-vector("list",length(KG_levs_CP))
pred_preds_CP <-vector("list",length(KG_levs_CP))
null_preds_CP <-vector("list",length(KG_levs_CP))
# Lists of predictions for each dataset

ref_k_CP <- vector("list",length(KG_levs_CP))
pred_k_CP <- vector("list",length(KG_levs_CP))
null_k_CP <- vector("list",length(KG_levs_CP))

for(i in 1:length(KG_levs_CP)) #KG_levs is the unique number of patch ids
{
  # For each one of if (!requireNamespace("devtools", quietly = TRUE)){install.packages("devtools")}   devtools::install_github("jbisanz/qiime2R")the patch ids, this is looping through.
  # If you want to trouble shoot this, put i = 1 into the r console and run line by line.
  # Patch id out, running the model, and predicting on the left out patch
 
  # Data use to fit the model
  KG_in_CP[[i]] <- KG_Magic_CP_use[-which(KG_Magic_CP_use$Patch_ID==KG_levs_CP[i]),]
 
  # Data used to test the model
  KG_out_CP[[i]] <- KG_Magic_CP_use[which(KG_Magic_CP_use$Patch_ID==KG_levs_CP[i]),]
 
  M0_KG_Magic_CP <- stan_glmer.nb(Bites~Season+(1|Patch_ID),data=KG_in_CP[[i]],cores=4, iter=10000)
 
  # Making predictions for the left out data
  null_preds_CP[[i]] <- posterior_predict(M0_KG_Magic_CP,newdata=KG_out_CP[[i]])
  null_k_CP[[i]] <- data.frame(M0_KG_Magic_CP)$reciprocal_dispersion
 
  mPRED_KG_Magic_CP <- stan_glmer.nb(Bites~Season+CP_Pred_std+(1|Patch_ID),data=KG_in_CP[[i]],cores=4, iter=10000)
 
  pred_preds_CP[[i]] <- posterior_predict(mPRED_KG_Magic_CP,newdata=KG_out_CP[[i]])
  pred_k_CP[[i]] <- data.frame(mPRED_KG_Magic_CP)$reciprocal_dispersion
 
  mREF_KG_Magic_CP <- stan_glmer.nb(Bites~Season+CP_Ref_std+(1|Patch_ID),data=KG_in_CP[[i]],cores=4)
 
  ref_preds_CP[[i]] <- posterior_predict(mPRED_KG_Magic_CP,newdata=KG_out_CP[[i]])
  ref_k_CP[[i]] <- data.frame(mREF_KG_Magic_CP)$reciprocal_dispersion
  }

# Extracting the predictions
# Binding the results together in a single data frame
KG_logo_CP <- vector("list",4)
names(KG_logo_CP) <- c("out_data","null","ref","pred")
KG_logo_CP[[1]] <- do.call("rbind",KG_out_CP)
KG_logo_CP[[2]] <- t(do.call("cbind",null_preds_CP))
KG_logo_CP[[3]] <- t(do.call("cbind",ref_preds_CP))
KG_logo_CP[[4]] <- t(do.call("cbind",pred_preds_CP))

KG_k_CP <- vector("list",4)
names(KG_k_CP) <- c("out_data","null","ref","pred")

KG_k_CP[[1]] <- do.call("rbind",KG_out_CP)
KG_k_CP[[2]] <- t(do.call("cbind",null_k_CP))
KG_k_CP[[3]] <- t(do.call("cbind",ref_k_CP))
KG_k_CP[[4]] <- t(do.call("cbind",pred_k_CP))

# Save the object
save(KG_k_CP,file="KG_k_CP.Rdata")

# Load(file="KG_logo_CP.Rdata")
str(KG_logo_CP)

# Predicted data
# These are the predictions from the three models above. These are matrices, because we are doing this in a Bayesian context. 
null_preds_CP <- KG_logo_CP$null
ref_preds_CP <- KG_logo_CP$ref
pred_preds_CP <-KG_logo_CP$pred

# New variable
KG_obs_CP<-KG_logo_CP$out_data$Bites

# New variable (not sure what this would be in KG_Magic)
KG_total_CP <- KG_logo_CP$out_data$Bites

# 1 = whether you're doing the mean across rows or columns
# Trying to predict across patchm, to create something in a list. 
KG_null_CP<-apply(null_preds_CP,1,mean)
length(KG_null_CP) #487
KG_ref_CP<-apply(ref_preds_CP,1,mean)
length(KG_ref_CP) #487
KG_pred_CP<-apply(pred_preds_CP,1,mean)
length(KG_pred_CP) #487

# Likelihood of observed data, given predicted data. 

# Mean absolute error, defined above. This is on the scale of the data, so the negative log likelihoods (which are a bit abstract) make more sense. 
mae(KG_null_CP,KG_obs_CP) #9.86572
mae(KG_ref_CP,KG_obs_CP) #10.92547
mae(KG_pred_CP, KG_obs_CP) #10.96559
```

# General posterior draw descriptive statistics

```{r}

nameo <- list.files()[-1]

chem_range <- read.csv("Text_Chemistry_Mins_Max_16Nov2025.csv")

load("mREF_KG_Magic_single_P.Rdata")
load("mPRED_KG_Magic_single_P.Rdata")
load("mREF_KG_Magic_single_M.Rdata")
load("mPRED_KG_Magic_single_M.Rdata")
load("mREF_KG_Magic_single_CP.Rdata")
load("mPRED_KG_Magic_single_CP.Rdata")

#All chemicals
chemm <- read.csv("Text_Chemistry_Mins_Max_16Nov2025.csv")

#First we will pull out the posterior draws:
#Phenolics
ref_KG_posteriors_P <- data.frame(mREF_KG_Magic_single_P)
pred_KG_posteriors_P <- data.frame(mPRED_KG_Magic_single_P)

#Monoterpenes
ref_KG_posteriors_M <- data.frame(mREF_KG_Magic_single_M)
pred_KG_posteriors_M <- data.frame(mPRED_KG_Magic_single_M)

#CP
ref_KG_posteriors_CP <- data.frame(mREF_KG_Magic_single_CP)
pred_KG_posteriors_CP <- data.frame(mPRED_KG_Magic_single_CP)

dim(ref_KG_posteriors_P) #20000    25
dim(pred_KG_posteriors_P) #20000    25
dim(ref_KG_posteriors_M) #20000    27
dim(pred_KG_posteriors_M) #20000    27
dim(ref_KG_posteriors_CP) #20000    27
dim(pred_KG_posteriors_CP) #20000    27

```

# Probability of Direction - Reference

What is the percentage of draws that are either positive of negative?

```{r}

# Crude Proteins
length(which(ref_KG_posteriors_CP$CP_Ref_std>0))/length(ref_KG_posteriors_CP$CP_Ref_std) #1
 
length(which(ref_KG_posteriors_CP$CP_Ref_std<0))/length(ref_KG_posteriors_CP$CP_Ref_std) #0

# Monoterpenes
length(which(ref_KG_posteriors_M$Monoterpenes_Ref_std>0))/length(ref_KG_posteriors_M$Monoterpenes_Ref_std) #0.00515

length(which(ref_KG_posteriors_M$Monoterpenes_Ref_std<0))/length(ref_KG_posteriors_M$Monoterpenes_Ref_std) #0.99485

# Phenolics
length(which(ref_KG_posteriors_P$Phenolics_Ref_std>0))/length(ref_KG_posteriors_P$Phenolics_Ref_std) #7e-04

length(which(ref_KG_posteriors_P$Phenolics_Ref_std<0))/length(ref_KG_posteriors_P$Phenolics_Ref_std) #0.9993

```

# Probability of Direction - Predicted Chemistry

What is the percentage of draws that are either positive of negative?

```{r}

# Crude Proteins
length(which(pred_KG_posteriors_CP$CP_Pred_std>0))/length(pred_KG_posteriors_CP$CP_Pred_std) #0.9999

length(which(pred_KG_posteriors_CP$CP_Pred_std<0))/length(pred_KG_posteriors_CP$CP_Pred_std) #1e-04

# Monoterpenes
length(which(pred_KG_posteriors_M$Monoterpenes_Pred_std>0))/length(pred_KG_posteriors_M$Monoterpenes_Pred_std) #0.0187

length(which(pred_KG_posteriors_M$Monoterpenes_Pred_std<0))/length(pred_KG_posteriors_M$Monoterpenes_Pred_std) #0.9813

# Phenolics
length(which(pred_KG_posteriors_P$Phenolics_Pred_std>0))/length(pred_KG_posteriors_P$Phenolics_Pred_std) #0.4755

length(which(pred_KG_posteriors_P$Phenolics_Pred_std<0))/length(pred_KG_posteriors_P$Phenolics_Pred_std) #0.5245

```

# Effect Size Min & Max - Reference Chemistry

```{r}

# Referencing min and max from data frame
chemm$Ref_Min[which(chemm$Site=="KG_Magic" & chemm$Chemical=="Crude Protein")] 
chemm$Ref_Max[which(chemm$Site=="KG_Magic" & chemm$Chemical=="Crude Protein")] 

# Setting up an empty vector to fill in with predictions
predicted_diff_Phenolics_ref <- rep(NA,times=ncol(ref_KG_posteriors_P))
predicted_diff_Monoterpenes_ref <- rep(NA,times=ncol(ref_KG_posteriors_M))
predicted_diff_cp_ref <- rep(NA,times=ncol(ref_KG_posteriors_CP))

# Phenolics
for(i in 1:ncol(ref_KG_posteriors_P)){

# This is just an intercept + slope*x. exp ensures it is a probability. We are looping over every value of the posterior draw to propagate uncertainty.
min_pred_P <- exp(ref_KG_posteriors_P$X.Intercept.[i]+ref_KG_posteriors_P$Phenolics_Ref_std[i]*chemm$Ref_Min[which(chemm$Site=="KG_Magic" & chemm$Chemical=="Phenolics")])
  
max_pred_P <- exp(ref_KG_posteriors_P$X.Intercept.[i]+ref_KG_posteriors_P$Phenolics_Ref_std[i]*chemm$Ref_Max[which(chemm$Site=="KG_Magic" & chemm$Chemical=="Phenolics")])
  
predicted_diff_Phenolics_ref[i] <- max_pred_P-min_pred_P # This is the difference we will store. feel free to reverse the order here, depending on what you want to report.
}  

quantile(predicted_diff_Phenolics_ref,c(0.025,0.5,0.975)) 
#      2.5%        50%      97.5% 
#-13.584453  -8.652583  -4.170438   

# Monoterpenes
for(i in 1:ncol(ref_KG_posteriors_M)){

# This is just an intercept + slope*x. exp ensures it is a probability. We are looping over every value of the posterior draw to propagate uncertainty.
min_pred_M <- exp(ref_KG_posteriors_M$X.Intercept.[i]+ref_KG_posteriors_M$Monoterpenes_Ref_std[i]*chemm$Ref_Min[which(chemm$Site=="KG_Magic" & chemm$Chemical=="Monoterpenes")])
  
max_pred_M <- exp(ref_KG_posteriors_M$X.Intercept.[i]+ref_KG_posteriors_M$Monoterpenes_Ref_std[i]*chemm$Ref_Max[which(chemm$Site=="KG_Magic" & chemm$Chemical=="Monoterpenes")])
  
predicted_diff_Monoterpenes_ref[i]<- max_pred_M-min_pred_M # This is the difference we will store. feel free to reverse the order here, depending on what you want to report.
}  

quantile(predicted_diff_Monoterpenes_ref,c(0.025,0.5,0.975)) 
#      2.5%        50%      97.5% 
#-17.672075  -6.605915  -1.431594 

# CP

for(i in 1:ncol(ref_KG_posteriors_CP)){

# This is just an intercept + slope*x. exp ensures it is a probability. We are looping over every value of the posterior draw to propagate uncertainty.
min_pred_CP <- exp(ref_KG_posteriors_CP$X.Intercept.[i]+ref_KG_posteriors_CP$CP_Ref_std[i]*chemm$Ref_Min[which(chemm$Site=="KG_Magic" & chemm$Chemical=="Crude Protein")])
  
max_pred_CP <- exp(ref_KG_posteriors_CP$X.Intercept.[i]+ref_KG_posteriors_CP$CP_Ref_std[i]*chemm$Ref_Max[which(chemm$Site=="KG_Magic" & chemm$Chemical=="Crude Protein")])
  
predicted_diff_cp_ref[i] <- max_pred_CP-min_pred_CP #This is the difference we will store. 
  }  

quantile(predicted_diff_cp_ref,c(0.025,0.5,0.975)) 
#      2.5%        50%      97.5% 
#  14.45729  49.17426 159.41638

```

# Effect Size Min & Max - Predicted Chemistry

```{r}

# Referencing min and max from data frame
chemm$Pred_Min[which(chemm$Site=="KG_Magic" & chemm$Chemical=="Crude Protein")] #-1.34902
chemm$Pred_Max[which(chemm$Site=="KG_Magic" & chemm$Chemical=="Crude Protein")] #2.00042

# Setting up an empty vector to fill in with predictions
predicted_diff_cp_pred <- rep(NA,times=ncol(pred_KG_posteriors_CP))
predicted_diff_Monoterpenes_pred <- rep(NA,times=ncol(pred_KG_posteriors_M))
predicted_diff_Phenolics_pred <- rep(NA,times=ncol(pred_KG_posteriors_P))

# Phenolics
for(i in 1:ncol(pred_KG_posteriors_P)){

# This is just an intercept + slope*x. exp ensures it is a probability. We are looping over every value of the posterior draw to propagate uncertainty.
min_pred_P <- exp(pred_KG_posteriors_P$X.Intercept.[i]+pred_KG_posteriors_P$Phenolics_Pred_std[i]*chemm$Pred_Min[which(chemm$Site=="KG_Magic" & chemm$Chemical=="Phenolics")])
  
max_pred_P <- exp(pred_KG_posteriors_P$X.Intercept.[i]+pred_KG_posteriors_P$Phenolics_Pred_std[i]*chemm$Pred_Max[which(chemm$Site=="KG_Magic" & chemm$Chemical=="Phenolics")])
  
predicted_diff_Phenolics_pred[i] <- max_pred_P-min_pred_P # This is the difference we will store. 
}  

quantile(predicted_diff_Phenolics_pred,c(0.025,0.5,0.975)) 
#      2.5%        50%      97.5% 
#-6.0048006  0.1607879  5.3396647 


# Monoterpenes
for(i in 1:ncol(pred_KG_posteriors_M)){

# This is just an intercept + slope*x. exp ensures it is a probability. We are looping over every value of the posterior draw to propagate uncertainty.
min_pred_M <- exp(pred_KG_posteriors_M$X.Intercept.[i]+pred_KG_posteriors_M$Monoterpenes_Pred_std[i]*chemm$Pred_Min[which(chemm$Site=="KG_Magic" & chemm$Chemical=="Monoterpenes")])
  
max_pred_M <- exp(pred_KG_posteriors_M$X.Intercept.[i]+pred_KG_posteriors_M$Monoterpenes_Pred_std[i]*chemm$Pred_Max[which(chemm$Site=="KG_Magic" & chemm$Chemical=="Monoterpenes")])
  
predicted_diff_Monoterpenes_pred[i] <- max_pred_M-min_pred_M # This is the difference we will store. 
}  

quantile(predicted_diff_Monoterpenes_pred,c(0.025,0.5,0.975)) 
#       2.5%         50%       97.5% 
#-60.517659 -16.111058  -3.653675 

# CP
for(i in 1:ncol(pred_KG_posteriors_CP)){

# This is just an intercept + slope*x. exp ensures it is a probability. We are looping over every value of the posterior draw to propagate uncertainty.
min_pred_CP <-exp(pred_KG_posteriors_CP$X.Intercept.[i]+pred_KG_posteriors_CP$CP_Pred_std[i]*chemm$Pred_Min[which(chemm$Site=="KG_Magic" & chemm$Chemical=="Crude Protein")])
  
max_pred_CP <- exp(pred_KG_posteriors_CP$X.Intercept.[i]+pred_KG_posteriors_CP$CP_Pred_std[i]*chemm$Pred_Max[which(chemm$Site=="KG_Magic" & chemm$Chemical=="Crude Protein")])
  
predicted_diff_cp_pred[i]<-max_pred_CP-min_pred_CP # This is the difference we will store. 
  }  

quantile(predicted_diff_cp_pred,c(0.025,0.5,0.975)) 
#     2.5%       50%     97.5% 
 #5.447717 32.567988 75.554162 

```


