---
title: "Chapter 2 - Bite Data - Chemistry - Predicted Chemistry at KG Magic Site"
output:
  pdf_document: default
  html_document: default
---

This R Markdown file will input data for the KG Magic (Magic = Camas Prairie) site and prepare it for three downstream analyses determining the effects of chemistry and predicted chemistry on bite data. Negative binomial distribution (check this). 

KG Magic is a pygmy rabbit site that sampled active mounds only - paired on (3x3 grid=9) and off mound (3x4 cardinal directions=12). Individual plant data is available for this site. Data was collected in Spring and Winter, and had no upper limit for the number of bites counted. A negative binomial distribution was used to analyze this data set.

In addition to these data, individual pellet counts within a meter of each individual shrub. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#Load libraries
library("rprojroot")
library("loo")
library("rstanarm")
options(mc.cores = parallel::detectCores())
library("ggplot2")
library("bayesplot")
theme_set(bayesplot::theme_default(base_family = "sans"))
library("MASS")
library("lme4")
library("brms")
library("rstanarm")
```

# Functions

These functions are used throughout the markdown, and include ways for evaluating predictive error and standardizing the inputs. 

## Root mean square error (RSME)
This shows the difference between an estimator and the values observed, and provides a measure of accuracy.

## Mean absolute error (MAE)
This is a measure of errors between paired observations expressing the same phenomenon, and is one of a number of ways of comparing forecasts with their eventual outcomes.

## Residual sum of squares (RSS)
This is a measure of discrepancy between the data (x) and the model (d). A small value indicates a good fit between the data and the model (0 is a perfect fit). This number can be infinite, as far as I'm aware.

## Total sum of squares (TSS)

This is the explained sum of squares plus the RSS. 

## R2

The proportion of variance explained by the model out of the total variance in the data (0-1). Closer to one means 100% fit. 

## splt

Tidies up the data by removing the double names

## stdize

Putting all of the covariates on the same scale 
http://www.stat.columbia.edu/~gelman/research/published/standardizing7.pdf


```{r}
# This first function is for root mean square, where m is the model predictions, and x is the data.
rmse <- function(m,x) 
{
  sqrt(mean((x-m)^2,na.rm=T))
}

# This function is for mean absolute error, where m is the model predictions, and x is the data. 
mae <- function(m,x)
{
  mean(abs(((x-m))),na.rm=T)
}

# This function is for residual sum of squares
RSS <- function(m,x) 
{
  sum((((m))-(x))^2)
}

# This function is for total sum of squares
TSS <- function(x) 
{
  sum(((x)-(mean(x)))^2)
  }

R2<-function(m,x,logo=F) {
  mors<-na.omit(data.frame(m,x))
  m<-mors$m
  x<-mors$x
  
  if(logo==F) {return(1-RSS(m,x)/TSS(x))} else {return(1-RSS1(m,x)/TSS1(x))}
}

# Split names
splt=function(x,split,num) {
  
  x<-as.character(x)
  p1=strsplit(x,split=split,fixed=T)
  p2=unlist(lapply(p1,"[",num))
  return(p2)
}

# Standardize covariates
stdize<-function(x) {(x-mean(x,na.rm=T))/(2*sd(x,na.rm=T))}

```

# Read in Files

In the input file for the KG Magic site, you'll see that the number of bites are taken from individual plants (as opposed to averaged across morphotypes).  

```{r}
# Main data set that includes all the sites, chemotype levels. We're setting periods and blank spaces to read in to R as NA:
BB <- read.csv("All_Datasheets.csv", na.strings=c("."," ","","NA"))
BB <- unique(BB)

# Subset to just the KG Magic site. 
KG<-subset(BB,BB$Site=="KGMagic")

# See the distribution of number of bites. You'll see there is no averaged data here. 
unique(KG$Bites)

## Check out the dimensions of the input data:
# Bites
length(KG$Bites)
table(KG$Bites)

# Season
table(KG$Season)

# Species
table(KG$Species)

# Plant height
table(KG$PlantSize)
# Not available at this site

# Patch type
table(KG$PatchType)

#Patch_ID here is the random effect

table(KG$Patch_ID)[-which(table(KG$Patch_ID)==0)]

# Standardize our covariates
# Putting all of the covariates on the same scale 
# http://www.stat.columbia.edu/~gelman/research/published/standardizing7.pdf
stdize<-function(x) {(x-mean(x,na.rm=T))/(2*sd(x,na.rm=T))}

KG$CP_Pred_std<-stdize(KG$CP_Pred)
KG$Phenolics_Pred_std<-stdize(KG$Phenolics_Pred)
KG$Monoterpenes_Pred_std<-stdize(KG$Monoterpenes_Pred)

KG$CP_Ref_std<-stdize(KG$CP_Ref)
KG$Phenolics_Ref_std<-stdize(KG$Phenolics_Ref)
KG$Monoterpenes_Ref_std<-stdize(KG$Monoterpenes_Ref)

KG$Patch_ID<-droplevels(as.factor(paste("p",KG$Patch_ID,sep="_")))

# Create the data set that we use moving forward
KG_use<-na.omit(data.frame(Bites=KG$Bites, CP_Pred_std=KG$CP_Pred_std,PatchType=KG$PatchType, Season=KG$Season, Phenolics_Pred_std=KG$Phenolics_Pred_std,Monoterpenes_Pred_std=KG$Monoterpenes_Pred_std,Patch_ID=KG$Patch_ID,CP_Ref_std=KG$CP_Ref_std,Phenolics_Ref_std=KG$Phenolics_Ref_std,Monoterpenes_Ref_std=KG$Monoterpenes_Ref_std))

## Check out the dimensions of the final data:
# Bites
length(KG_use$Bites)
table(KG_use$Bites)

# Season
table(KG_use$Season)

# Patch type
table(KG_use$PatchType)

min(KG_use$CP_Ref_std)
max(KG_use$CP_Ref_std)

min(KG_use$CP_Pred_std) 
max(KG_use$CP_Pred_std)

min(KG_use$Phenolics_Ref_std) 
max(KG_use$Phenolics_Ref_std) 

min(KG_use$Phenolics_Pred_std)
max(KG_use$Phenolics_Pred_std)

min(KG_use$Monoterpenes_Ref_std)
max(KG_use$Monoterpenes_Ref_std)

min(KG_use$Monoterpenes_Pred_std)
max(KG_use$Monoterpenes_Pred_std)

## Descriptive Stats

# Crude Proteins

mean(KG$CP_Ref, na.rm=TRUE)
sd(KG$CP_Ref, na.rm=TRUE)

mean(KG$CP_Pred, na.rm=TRUE)
sd(KG$CP_Pred, na.rm=TRUE)

mean(KG_use$CP_Ref_std, na.rm=TRUE)
sd(KG_use$CP_Ref_std, na.rm=TRUE)

mean(KG_use$CP_Pred_std, na.rm=TRUE)
sd(KG_use$CP_Pred_std, na.rm=TRUE)

# Monoterpenes
mean(KG$Monoterpenes_Ref, na.rm=TRUE) 
sd(KG$Monoterpenes_Ref, na.rm=TRUE) 

mean(KG$Monoterpenes_Pred, na.rm=TRUE) 
sd(KG$Monoterpenes_Pred, na.rm=TRUE)

mean(KG_use$Monoterpenes_Ref_std, na.rm=TRUE)
sd(KG_use$Monoterpenes_Ref_std, na.rm=TRUE)

mean(KG_use$Monoterpenes_Pred_std, na.rm=TRUE)
sd(KG_use$Monoterpenes_Pred_std, na.rm=TRUE)

# Phenolics
mean(KG$Phenolics_Ref, na.rm=TRUE)
sd(KG$Phenolics_Ref, na.rm=TRUE)

mean(KG$Phenolics_Pred, na.rm=TRUE)
sd(KG$Phenolics_Pred, na.rm=TRUE)

mean(KG_use$Phenolics_Ref_std, na.rm=TRUE)
sd(KG_use$Phenolics_Ref_std, na.rm=TRUE)

mean(KG_use$Phenolics_Pred_std, na.rm=TRUE)
sd(KG_use$Phenolics_Pred_std, na.rm=TRUE)

```

# Question 1: what are the effects of chemistry on bites?

```{r}

#.nb = negative binomial
mREF_KG_Magic_single<-rstanarm::stan_glmer.nb(Bites~Season+CP_Ref_std+Phenolics_Ref_std+Monoterpenes_Ref_std+(1|Patch_ID),data=KG_use,cores=4, iter=10000)

summary(mREF_KG_Magic_single)

png(file="./KG_Magic_Reference.png")
plot(mREF_KG_Magic_single,regex_pars="_std")
dev.off()

save(mREF_KG_Magic_single, file = "mREF_KG_Magic_single.Rdata")

##############
# Extract posteriors

KG_Magic_single_REF <- as.data.frame(mREF_KG_Magic_single)

Phenolics_out <- KG_Magic_single_REF$Phenolics_Ref_std
Phenolics_REF_cat <- rep("Phenolics_REF",times=length(Phenolics_out))

CP_out <- KG_Magic_single_REF$CP_Ref_std
CP_REF_cat <- rep("CP_REF",times=length(CP_out))

Monoterpenes_out <- KG_Magic_single_REF$Monoterpenes_Ref_std
Monoterpenes_REF_cat <- rep("Monoterpenes_REF",times=length(Monoterpenes_out))

pos_draws <- c(Phenolics_out,CP_out,Monoterpenes_out)

chem_type <- c(Phenolics_REF_cat,CP_REF_cat,Monoterpenes_REF_cat)

KG_Magic_single_REF <- data.frame(pos_draws,chem_type)

KG_Magic_single_REF$Site<-rep("KG_Magic",times=nrow(KG_Magic_single_REF))

save(KG_Magic_single_REF ,file="KG_Magic_single_REF.Rdata")

```

# Question 2: does inference on chemistry effects change when using predicted, rather than observed values?

```{r}

mPRED_KG_Magic_single <-rstanarm::stan_glmer.nb(Bites~Season+CP_Pred_std+Phenolics_Pred_std+Monoterpenes_Pred_std+(1|Patch_ID),data=KG_use,cores=4,iter=10000)

summary(mPRED_KG_Magic_single)

png(file="./KG_Magic_Predicted.png")
plot(mPRED_KG_Magic_single,regex_pars="_std")
dev.off()

save(mPRED_KG_Magic_single, file = "mPRED_KG_Magic_single.Rdata")

##############
# Extract posteriors

KG_Magic_single_PRED <- as.data.frame(mPRED_KG_Magic_single)

Phenolics_out <- KG_Magic_single_PRED$Phenolics_Pred_std
Phenolics_PRED_cat <- rep("Phenolics_PRED",times=length(Phenolics_out))

CP_out <- KG_Magic_single_PRED$CP_Pred_std
CP_PRED_cat <- rep("CP_PRED",times=length(CP_out))

Monoterpenes_out <- KG_Magic_single_PRED$Monoterpenes_Pred_std
Monoterpenes_PRED_cat <- rep("Monoterpenes_PRED",times=length(Monoterpenes_out))

pos_draws <- c(Phenolics_out,CP_out,Monoterpenes_out)

chem_type <- c(Phenolics_PRED_cat,CP_PRED_cat,Monoterpenes_PRED_cat)

KG_Magic_single_PRED <- data.frame(pos_draws,chem_type)

KG_Magic_single_PRED$Site<-rep("KG_Magic",times=nrow(KG_Magic_single_PRED))

save(KG_Magic_single_PRED ,file="KG_Magic_single_PRED.Rdata")

```

# Question 3: how does the predictions changes when using obs vs predicted chemistry?

# https://onlinelibrary.wiley.com/doi/full/10.1111/ecog.02881
#paper that describes our leave-one-out approach

```{r}

# In this code, we are creating subsets of the data
KG_levs<-unique(KG_use$Patch_ID)
KG_in<-vector("list",length(KG_levs))
KG_out<-vector("list",length(KG_levs))

# We are testing three different models:
# Model 1 is the observed chemistry
# Model 2 is the predicted chemistry
# Model 3 is a null model with no chemistry
ref_preds<-vector("list",length(KG_levs))
pred_preds<-vector("list",length(KG_levs))
null_preds<-vector("list",length(KG_levs))
# Lists of predictions for each dataset

ref_k<-vector("list",length(KG_levs))
pred_k<-vector("list",length(KG_levs))
null_k<-vector("list",length(KG_levs))

for(i in 1:length(KG_levs)) #KG_levs is the unique number of patch ids
{
  # For each one of if (!requireNamespace("devtools", quietly = TRUE)){install.packages("devtools")}   devtools::install_github("jbisanz/qiime2R")the patch ids, this is looping through.
  # If you want to trouble shoot this, put i = 1 into the r console and run line by line.
  # Patch id out, running the model, and predicting on the left out patch
 
  # Data use to fit the model
  KG_in[[i]]<-KG_use[-which(KG_use$Patch_ID==KG_levs[i]),]
 
  # Data used to test the model
  KG_out[[i]]<-KG_use[which(KG_use$Patch_ID==KG_levs[i]),]
 
  M0_KG_Magic<-stan_glmer.nb(Bites~Season+(1|Patch_ID),data=KG_in[[i]],cores=4, iter=10000)
 
  # Making predictions for the left out data
  null_preds[[i]]=posterior_predict(M0_KG_Magic,newdata=KG_out[[i]])
  null_k[[i]]=data.frame(M0_KG_Magic)$reciprocal_dispersion
 
 
  mPRED_KG_Magic<-stan_glmer.nb(Bites~Season+CP_Pred_std+Phenolics_Pred_std+Monoterpenes_Pred_std+(1|Patch_ID),data=KG_in[[i]],cores=4, iter=10000)
 
  pred_preds[[i]]=posterior_predict(mPRED_KG_Magic,newdata=KG_out[[i]])
  pred_k[[i]]=data.frame(mPRED_KG_Magic)$reciprocal_dispersion
 
  mREF_KG_Magic<-stan_glmer.nb(Bites~Season+CP_Ref_std+Phenolics_Ref_std+Monoterpenes_Ref_std+(1|Patch_ID),data=KG_in[[i]],cores=4)
 
  ref_preds[[i]]<-posterior_predict(mPRED_KG_Magic,newdata=KG_out[[i]])
  ref_k[[i]]=data.frame(mREF_KG_Magic)$reciprocal_dispersion
  }

# Extracting the predictions
# Binding the results together in a single data frame
KG_logo<-vector("list",4)
names(KG_logo)<-c("out_data","null","ref","pred")
KG_logo[[1]]<-do.call("rbind",KG_out)
KG_logo[[2]]<-t(do.call("cbind",null_preds))
KG_logo[[3]]<-t(do.call("cbind",ref_preds))
KG_logo[[4]]<-t(do.call("cbind",pred_preds))

KG_k<-vector("list",4)
names(KG_k)<-c("out_data","null","ref","pred")

KG_k[[1]]<-do.call("rbind",KG_out)
KG_k[[2]]<-t(do.call("cbind",null_k))
KG_k[[3]]<-t(do.call("cbind",ref_k))
KG_k[[4]]<-t(do.call("cbind",pred_k))

# Save the object
save(KG_k,file="KG_k.Rdata")

# Load(file="KG_logo.Rdata")
str(KG_logo)

# Predicted data
# These are the predictions from the three models above. These are matrices, because we are doing this in a Bayesian context. 
null_preds=KG_logo$null

ref_preds=KG_logo$ref

pred_preds=KG_logo$pred

# New variable
KG_obs<-KG_logo$out_data$Bites

# New variable (not sure what this would be in KG_Magic)
KG_total <- KG_logo$out_data$Bites

# 1 = whether you're doing the mean across rows or columns
# Trying to predict across patchm, to create something in a list. 
KG_null<-apply(null_preds,1,mean)
length(KG_null)
KG_ref<-apply(ref_preds,1,mean)
length(KG_ref)
KG_pred<-apply(pred_preds,1,mean)
length(KG_pred)

# Likelihood of observed data, given predicted data. 

# Mean absolute error, defined above. This is on the scale of the data, so the negative log likelihoods (which are a bit abstract) make more sense. 
mae(KG_null,KG_obs)
mae(KG_ref,KG_obs)
mae(KG_pred, KG_obs)
#13.33732

```

# General posterior draw descriptive statistics

```{r}

nameo <- list.files()[-1]

chem_range <- read.csv("Text_Chemistry_Mins_Max_13July2023.csv")

load("mREF_KG_Magic_single.Rdata")
load("mPRED_KG_Magic_single.Rdata")

#All chemicals
chemm <- read.csv("Text_Chemistry_Mins_Max_13July2023.csv")

#First we will pull out the posterior draws:
ref_KG_posteriors <- data.frame(mREF_KG_Magic_single)
pred_KG_posteriors <- data.frame(mPRED_KG_Magic_single)

dim(ref_KG_posteriors)
dim(pred_KG_posteriors)

```

# Probability of Direction - Reference

What is the percentage of draws that are either positive of negative?

```{r}

# Crude Proteins
length(which(ref_KG_posteriors$CP_Ref_std>0))/length(ref_KG_posteriors$CP_Ref_std)
 
length(which(ref_KG_posteriors$CP_Ref_std<0))/length(ref_KG_posteriors$CP_Ref_std)

# Monoterpenes
length(which(ref_KG_posteriors$Monoterpenes_Ref_std>0))/length(ref_KG_posteriors$Monoterpenes_Ref_std)

length(which(ref_KG_posteriors$Monoterpenes_Ref_std<0))/length(ref_KG_posteriors$Monoterpenes_Ref_std)

# Phenolics
length(which(ref_KG_posteriors$Phenolics_Ref_std>0))/length(ref_KG_posteriors$Phenolics_Ref_std)

length(which(ref_KG_posteriors$Phenolics_Ref_std<0))/length(ref_KG_posteriors$Phenolics_Ref_std)

```

# Probability of Direction - Predicted Chemistry

What is the percentage of draws that are either positive of negative?

```{r}

# Crude Proteins
length(which(pred_KG_posteriors$CP_Pred_std>0))/length(pred_KG_posteriors$CP_Pred_std)

length(which(pred_KG_posteriors$CP_Pred_std<0))/length(pred_KG_posteriors$CP_Pred_std)

# Monoterpenes
length(which(pred_KG_posteriors$Monoterpenes_Pred_std>0))/length(pred_KG_posteriors$Monoterpenes_Pred_std)

length(which(pred_KG_posteriors$Monoterpenes_Pred_std<0))/length(pred_KG_posteriors$Phenolics_Pred_std)

# Phenolics
length(which(pred_KG_posteriors$Phenolics_Pred_std>0))/length(pred_KG_posteriors$Phenolics_Pred_std)

length(which(pred_KG_posteriors$Phenolics_Pred_std<0))/length(pred_KG_posteriors$Phenolics_Pred_std)

```

# Effect Size Min & Max - Reference Chemistry

```{r}

# Referencing min and max from data frame
chemm$Ref_Min[which(chemm$Site=="KG_Magic" & chemm$Chemical=="Crude Protein")] 
chemm$Ref_Max[which(chemm$Site=="KG_Magic" & chemm$Chemical=="Crude Protein")] 

# Setting up an empty vector to fill in with predictions
predicted_diff_cp_ref <- rep(NA,times=ncol(ref_KG_posteriors))
predicted_diff_Monoterpenes_ref <- rep(NA,times=ncol(ref_KG_posteriors))
predicted_diff_Phenolics_ref <- rep(NA,times=ncol(ref_KG_posteriors))

# CP

for(i in 1:ncol(ref_KG_posteriors)){

# This is just an intercept + slope*x. exp ensures it is a probability. We are looping over every value of the posterior draw to propagate uncertainty.
min_pred<-exp(ref_KG_posteriors$X.Intercept.[i]+ref_KG_posteriors$CP_Ref_std[i]*chemm$Ref_Min[which(chemm$Site=="KG_Magic" & chemm$Chemical=="Crude Protein")])
  
max_pred<-exp(ref_KG_posteriors$X.Intercept.[i]+ref_KG_posteriors$CP_Ref_std[i]*chemm$Ref_Max[which(chemm$Site=="KG_Magic" & chemm$Chemical=="Crude Protein")])
  
predicted_diff_cp_ref[i]<-max_pred-min_pred #This is the difference we will store. 
  }  

quantile(predicted_diff_cp_ref,c(0.025,0.5,0.975)) 

# Monoterpenes
for(i in 1:ncol(ref_KG_posteriors)){

# This is just an intercept + slope*x. exp ensures it is a probability. We are looping over every value of the posterior draw to propagate uncertainty.
min_pred<-exp(ref_KG_posteriors$X.Intercept.[i]+ref_KG_posteriors$Monoterpenes_Ref_std[i]*chemm$Ref_Min[which(chemm$Site=="KG_Magic" & chemm$Chemical=="Monoterpenes")])
  
max_pred<-exp(ref_KG_posteriors$X.Intercept.[i]+ref_KG_posteriors$Monoterpenes_Ref_std[i]*chemm$Ref_Max[which(chemm$Site=="KG_Magic" & chemm$Chemical=="Monoterpenes")])
  
predicted_diff_Monoterpenes_ref[i]<-max_pred-min_pred # This is the difference we will store. feel free to reverse the order here, depending on what you want to report.
}  

quantile(predicted_diff_Monoterpenes_ref,c(0.025,0.5,0.975)) 

# Phenolics
for(i in 1:ncol(ref_KG_posteriors)){

# This is just an intercept + slope*x. exp ensures it is a probability. We are looping over every value of the posterior draw to propagate uncertainty.
min_pred<-exp(ref_KG_posteriors$X.Intercept.[i]+ref_KG_posteriors$Phenolics_Ref_std[i]*chemm$Ref_Min[which(chemm$Site=="KG_Magic" & chemm$Chemical=="Phenolics")])
  
max_pred<-exp(ref_KG_posteriors$X.Intercept.[i]+ref_KG_posteriors$Phenolics_Ref_std[i]*chemm$Ref_Max[which(chemm$Site=="KG_Magic" & chemm$Chemical=="Phenolics")])
  
predicted_diff_Phenolics_ref[i]<-max_pred-min_pred # This is the difference we will store. 
}  

quantile(predicted_diff_Phenolics_ref,c(0.025,0.5,0.975)) 
 
```

# Effect Size Min & Max - Predicted Chemistry

```{r}

# Referencing min and max from data frame
chemm$Pred_Min[which(chemm$Site=="KG_Magic" & chemm$Chemical=="Crude Protein")] 
chemm$Pred_Max[which(chemm$Site=="KG_Magic" & chemm$Chemical=="Crude Protein")] 

# Setting up an empty vector to fill in with predictions
predicted_diff_cp_pred <- rep(NA,times=ncol(pred_KG_posteriors))
predicted_diff_Monoterpenes_pred <- rep(NA,times=ncol(pred_KG_posteriors))
predicted_diff_Phenolics_pred <- rep(NA,times=ncol(pred_KG_posteriors))

# CP
for(i in 1:ncol(pred_KG_posteriors)){

# This is just an intercept + slope*x. exp ensures it is a probability. We are looping over every value of the posterior draw to propagate uncertainty.
min_pred<-exp(pred_KG_posteriors$X.Intercept.[i]+pred_KG_posteriors$CP_Pred_std[i]*chemm$Pred_Min[which(chemm$Site=="KG_Magic" & chemm$Chemical=="Crude Protein")])
  
max_pred<-exp(pred_KG_posteriors$X.Intercept.[i]+pred_KG_posteriors$CP_Pred_std[i]*chemm$Pred_Max[which(chemm$Site=="KG_Magic" & chemm$Chemical=="Crude Protein")])
  
predicted_diff_cp_pred[i]<-max_pred-min_pred # This is the difference we will store. 
  }  

quantile(predicted_diff_cp_pred,c(0.025,0.5,0.975)) 

# Monoterpenes
for(i in 1:ncol(pred_KG_posteriors)){

# This is just an intercept + slope*x. exp ensures it is a probability. We are looping over every value of the posterior draw to propagate uncertainty.
min_pred<-exp(pred_KG_posteriors$X.Intercept.[i]+pred_KG_posteriors$Monoterpenes_Pred_std[i]*chemm$Pred_Min[which(chemm$Site=="KG_Magic" & chemm$Chemical=="Monoterpenes")])
  
max_pred<-exp(pred_KG_posteriors$X.Intercept.[i]+pred_KG_posteriors$Monoterpenes_Pred_std[i]*chemm$Pred_Max[which(chemm$Site=="KG_Magic" & chemm$Chemical=="Monoterpenes")])
  
predicted_diff_Monoterpenes_pred[i]<-max_pred-min_pred # This is the difference we will store. 
}  

quantile(predicted_diff_Monoterpenes_pred,c(0.025,0.5,0.975)) 

# Phenolics
for(i in 1:ncol(pred_KG_posteriors)){

# This is just an intercept + slope*x. exp ensures it is a probability. We are looping over every value of the posterior draw to propagate uncertainty.
min_pred<-exp(pred_KG_posteriors$X.Intercept.[i]+pred_KG_posteriors$Phenolics_Pred_std[i]*chemm$Pred_Min[which(chemm$Site=="KG_Magic" & chemm$Chemical=="Phenolics")])
  
max_pred<-exp(pred_KG_posteriors$X.Intercept.[i]+pred_KG_posteriors$Phenolics_Pred_std[i]*chemm$Pred_Max[which(chemm$Site=="KG_Magic" & chemm$Chemical=="Phenolics")])
  
predicted_diff_Phenolics_pred[i]<-max_pred-min_pred # This is the difference we will store. 
}  

quantile(predicted_diff_Phenolics_pred,c(0.025,0.5,0.975)) 

```


