---
title: "Chapter 2 - Bite Data - Chemistry - Predicted Chemistry at Raft River Site"
output:
  pdf_document: default
  html_document: default
---

This R Markdown file will input data for the Raft River site and prepare it for three downstream analyses determining the effects of chemistry and predicted chemistry on bite data. 

Raft River is a Greater Sage-grouse site that sampled using a stratified random (within patch boundary) using 3 plants for each morphotype (size + species) for browsed and unbrowsed plants at each patch pooled into each sample. All samples were pooled for chemistry per morphotype, but bite mark data exists for individual plants through Marcella's data. Data was collected in Winter only. There is an upper limit of 50 bites for some of these individuals, so proportional data was used with an upper limit of 50. A binomial distribution was used to analyze this data set.

In addition to these data, individual pellet counts within a meter of each individual shrub. 

# Input libraries

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#Load libraries
library("rprojroot")
library("loo")
library("rstanarm")
options(mc.cores = parallel::detectCores())
library("ggplot2")
library("bayesplot")
theme_set(bayesplot::theme_default(base_family = "sans"))
library("MASS")
library("lme4")
library("brms")
library("rstanarm")
```

# Functions

These functions are used throughout the markdown, and include ways for evaluating predictive error and standardizing the inputs. 

## Root mean square error (RSME)
This shows the difference between an estimator and the values observed, and provides a measure of accuracy.

## Mean absolute error (MAE)
This is a measure of errors between paired observations expressing the same phenomenon, and is one of a number of ways of comparing forecasts with their eventual outcomes.

## Residual sum of squares (RSS)
This is a measure of discrepancy between the data (x) and the model (d). A small value indicates a good fit between the data and the model (0 is a perfect fit). This number can be infinite, as far as I'm aware.

## Total sum of squares (TSS)

This is the explained sum of squares plus the RSS. 

## R2

The proportion of variance explained by the model out of the total variance in the data (0-1). Closer to one means 100% fit. 

## splt

Tidies up the data by removing the double names

## stdize

Putting all of the covariates on the same scale 
http://www.stat.columbia.edu/~gelman/research/published/standardizing7.pdf

```{r}
# This first function is for root mean square, where m is the model predictions, and x is the data.
rmse <- function(m,x) 
{
  sqrt(mean((x-m)^2,na.rm=T))
}

# This function is for mean absolute error, where m is the model predictions, and x is the data. 
mae <- function(m,x)
{
  mean(abs(((x-m))),na.rm=T)
}

# This function is for residual sum of squares
RSS <- function(m,x) 
{
  sum((((m))-(x))^2)
}

# This function is for total sum of squares
TSS <- function(x) 
{
  sum(((x)-(mean(x)))^2)
  }

R2<-function(m,x,logo=F) {
  mors<-na.omit(data.frame(m,x))
  m<-mors$m
  x<-mors$x
  
  if(logo==F) {return(1-RSS(m,x)/TSS(x))} else {return(1-RSS1(m,x)/TSS1(x))}
}

# Split names
splt=function(x,split,num) {
  
  x<-as.character(x)
  p1=strsplit(x,split=split,fixed=T)
  p2=unlist(lapply(p1,"[",num))
  return(p2)
}

# Standardize covariates
stdize<-function(x) {(x-mean(x,na.rm=T))/(2*sd(x,na.rm=T))}
```

# Read in Files

In All_Datasheets.csv, you will see that bites is an average for each small cluster of plants - or 'morphotypes'. For Marcella's bite file (mbites), we get a 'raw' bite count on a per plant basis. Because some of the bites are 'binned' after 50, a cutoff of 50 bites is used for this data set. 

Note, we are using a binomial distribution for bite data here. This will have to be done with pooled samples. 

```{r}
# Main data set that includes all the sites, chemotype levels. We're setting periods and blank spaces to read in to R as NA:
. 
BB <- read.csv("All_Datasheets.csv", na.strings=c("."," ","","NA"))
BB <- unique(BB)

# Marcella's table includes bite data from individual plants
mbites<-read.csv("marcella_bites.csv",na.strings=c("."," ","","NA"))

# Define the number of trials for the binomial distribution. We set the maximum number of bite marks here as 50.
mbites$bites_binomial<-ifelse(mbites$bite_marks>50,50,mbites$bite_marks)

# Additional lines to process and make sure the data is not characters or no-integer data or anything like that:
bite_out<-mbites[which(is.na(mbites$bites_binomial)==F),]
mbit<-mbites[which(is.na(bite_out$Sample)==F),]

# Subset of the big Brecken bite data that only is the Raft River site:
RR<-subset(BB,BB$Site=="Raft River") 

# The sample is the unique identifier for individual plants, so we can merge Marcella's data (raw bites) and Brecken's data (average bites + values for chemistry) using this information. 
raft_river=merge(RR,mbit,by.x="Sample",by.y="Sample") 

## Check out the dimensions of the input data:
# Bites
length(raft_river$Bites)
table(raft_river$Bites)
# Wide distribution of bites that are averaged across morphotype 

# Season
table(raft_river$Season)

# Species
table(raft_river$Species)

# Plant height
table(raft_river$PlantSize)

table(raft_river$PatchType)

#Patch_ID here is the random effect.

table(raft_river$Patch_ID.x)[-which(table(raft_river$Patch_ID.x)==0)] 

# Standardize our covariates
stdize<-function(x) {(x-mean(x,na.rm=TRUE))/(2*sd(x,na.rm=TRUE))}

raft_river$CP_Pred_std<-stdize(raft_river$CP_Pred)
raft_river$Phenolics_Pred_std<-stdize(raft_river$Phenolics_Pred)
raft_river$Monoterpenes_Pred_std<-stdize(raft_river$Monoterpenes_Pred)

raft_river$CP_Ref_std<-stdize(raft_river$CP_Ref)
raft_river$Phenolics_Ref_std<-stdize(raft_river$Phenolics_Ref)
raft_river$Monoterpenes_Ref_std<-stdize(raft_river$Monoterpenes_Ref)

raft_river$Patch_ID<-droplevels(as.factor(paste("p",raft_river$Patch_ID.x,sep="_")))

raft_river_use<-na.omit(data.frame(Bites=raft_river$bites_binomial,CP_Pred_std=raft_river$CP_Pred_std,PatchType=raft_river$Patch_ID,Phenolics_Pred_std=raft_river$Phenolics_Pred_std,Monoterpenes_Pred_std=raft_river$Monoterpenes_Pred_std, Patch_ID=raft_river$Patch_ID,CP_Ref_std=raft_river$CP_Ref_std,Phenolics_Ref_std=raft_river$Phenolics_Ref_std,Monoterpenes_Ref_std=raft_river$Monoterpenes_Ref_std))
                                
# Creating a proprotional variable to help visualize the data
raft_river_use$bprop<-raft_river_use$Bites/50 #since 50 is the max

# This is a how binomial proportional data are read into R
# This is creating a matrix with the two important details for binomial regression the number of 
# Successes and the number of failures. 
raft_river_bound<-cbind(raft_river_use$Bites,50-raft_river_use$Bites)
raft_river_use$raft_river_bound<-raft_river_bound

## Check out the dimensions of the final data:
# Bites
length(raft_river_use$Bites) 
table(raft_river_use$Bites)

# Season
table(raft_river_use$Season)

# Patch type
table(raft_river_use$PatchType)

min(raft_river_use$CP_Ref_std)
max(raft_river_use$CP_Ref_std)

min(raft_river_use$CP_Pred_std)
max(raft_river_use$CP_Pred_std)

min(raft_river_use$Phenolics_Ref_std)
max(raft_river_use$Phenolics_Ref_std)

min(raft_river_use$Phenolics_Pred_std)
max(raft_river_use$Phenolics_Pred_std)

min(raft_river_use$Monoterpenes_Ref_std)
max(raft_river_use$Monoterpenes_Ref_std)

min(raft_river_use$Monoterpenes_Pred_std)
max(raft_river_use$Monoterpenes_Pred_std)

## Descriptive Stats

# Crude Proteins

mean(raft_river$CP_Ref, na.rm=TRUE)
sd(raft_river$CP_Ref, na.rm=TRUE)

mean(raft_river$CP_Pred, na.rm=TRUE)
sd(raft_river$CP_Pred, na.rm=TRUE)

mean(raft_river_use$CP_Ref_std, na.rm=TRUE)
sd(raft_river_use$CP_Ref_std, na.rm=TRUE)

mean(raft_river_use$CP_Pred_std, na.rm=TRUE)
sd(raft_river_use$CP_Pred_std, na.rm=TRUE)

# Monoterpenes
mean(raft_river$Monoterpenes_Ref, na.rm=TRUE)
sd(raft_river$Monoterpenes_Ref, na.rm=TRUE)

mean(raft_river$Monoterpenes_Pred, na.rm=TRUE)
sd(raft_river$Monoterpenes_Pred, na.rm=TRUE)

mean(raft_river_use$Monoterpenes_Ref_std, na.rm=TRUE)
sd(raft_river_use$Monoterpenes_Ref_std, na.rm=TRUE)

mean(raft_river_use$Monoterpenes_Pred_std, na.rm=TRUE)
sd(raft_river_use$Monoterpenes_Pred_std, na.rm=TRUE)

# Phenolics
mean(raft_river$Phenolics_Ref, na.rm=TRUE)
sd(raft_river$Phenolics_Ref, na.rm=TRUE)

mean(raft_river$Phenolics_Pred, na.rm=TRUE)
sd(raft_river$Phenolics_Pred, na.rm=TRUE)

mean(raft_river_use$Phenolics_Ref_std, na.rm=TRUE)
sd(raft_river_use$Phenolics_Ref_std, na.rm=TRUE)

mean(raft_river_use$Phenolics_Pred_std, na.rm=TRUE)
sd(raft_river_use$Phenolics_Pred_std, na.rm=TRUE)
```

# Question 1: what are the effects of chemistry on bites?

```{r}
mREF_RR_single=stan_glmer(raft_river_bound~CP_Ref_std+Phenolics_Ref_std+Monoterpenes_Ref_std+(1|Patch_ID),data=raft_river_use,cores=4,family="binomial",iter=10000)

summary(mREF_RR_single)

png(file="./RR_Reference.png")
plot(mREF_RR_single,regex_pars="_std")
dev.off()

save(mREF_RR_single, file = "mREF_RR_single.Rdata")

##############
# Extract posteriors

RR_single_REF <- as.data.frame(mREF_RR_single)

Phenolics_out <- RR_single_REF$Phenolics_Ref_std
Phenolics_REF_cat <- rep("Phenolics_REF",times=length(Phenolics_out))

CP_out <- RR_single_REF$CP_Ref_std
CP_REF_cat <- rep("CP_REF",times=length(CP_out))

Monoterpenes_out <- RR_single_REF$Monoterpenes_Ref_std
Monoterpenes_REF_cat <- rep("Monoterpenes_REF",times=length(Monoterpenes_out))

pos_draws <- c(Phenolics_out,CP_out, Monoterpenes_out)

chem_type <- c(Phenolics_REF_cat,CP_REF_cat, Monoterpenes_REF_cat)

RR_single_REF <- data.frame(pos_draws,chem_type)

RR_single_REF$Site<-rep("RR",times=nrow(RR_single_REF))

save(RR_single_REF ,file="RR_single_REF.Rdata")
```

# Question 2: does inference on chemistry effects change when using predicted, rather than observed values?

```{r}

# The effective size of this model is too small, so we increased the number of iterations from 2K (standard) to 10K. 
mPRED_RR_single =stan_glmer(raft_river_bound~CP_Pred_std+Phenolics_Pred_std+Monoterpenes_Pred_std+(1|Patch_ID),data=raft_river_use,cores=4,family="binomial", iter=10000)

summary(mPRED_RR_single)

png(file="./RR_Pred.png")
plot(mPRED_RR_single,regex_pars="Pred")
dev.off()

save(mPRED_RR_single, file = "mPRED_RR_single.Rdata")

#From this plot, we can see whether predicted chemistry agrees with empirical chemistry.

RR_single_PRED <- as.data.frame(mPRED_RR_single)

Phenolics_out <- RR_single_PRED$Phenolics_Pred_std
Phenolics_PRED_cat <- rep("Phenolics_PRED",times=length(Phenolics_out))

CP_out <- RR_single_PRED$CP_Pred_std
CP_PRED_cat <- rep("CP_PRED",times=length(CP_out))

Monoterpenes_out <- RR_single_PRED$Monoterpenes_Pred_std
Monoterpenes_PRED_cat <- rep("Monoterpenes_PRED",times=length(Monoterpenes_out))

pos_draws <- c(Phenolics_out,CP_out, Monoterpenes_out)

chem_type <- c(Phenolics_PRED_cat,CP_PRED_cat, Monoterpenes_PRED_cat)

RR_single_PRED <- data.frame(pos_draws,chem_type)

RR_single_PRED$Site<-rep("RR",times=nrow(RR_single_PRED))

save(RR_single_PRED ,file="RR_single_PRED.Rdata")

```

#Question 3: how does the predictions changes when using obs vs predicted chemistry?

#https://onlinelibrary.wiley.com/doi/full/10.1111/ecog.02881
#paper that describes our leave-one-out approach

```{r}
# In this code, we are creating subsets of the data
raft_river_levs<-unique(raft_river_use$Patch_ID)
raft_river_in<-vector("list",length(raft_river_levs))
raft_river_out<-vector("list",length(raft_river_levs))

# We are testing three different models:
# Model 1 is the observed chemistry
# Model 2 is the predicted chemistry
# Model 3 is a null model with no chemistry
ref_preds<-vector("list",length(raft_river_levs))
pred_preds<-vector("list",length(raft_river_levs))
null_preds<-vector("list",length(raft_river_levs))
#lists of predictions for each dataset

for(i in 1:length(raft_river_levs)) #raft_river_levs is the unique number of patch ids
{
  # For each one of if (!requireNamespace("devtools", quietly = TRUE)){install.packages("devtools")}   devtools::install_github("jbisanz/qiime2R")the patch ids, this is looping through. 
  # If you want to trouble shoot this, put i = 1 into the r consul and run line by line. 
  # Patch id out, running the model, and predicting on the left out patch
  
  # Data use to fit the model
  raft_river_in[[i]]<-raft_river_use[-which(raft_river_use$Patch_ID==raft_river_levs[i]),]
  
   # Data used to test the model
  raft_river_out[[i]]<-raft_river_use[which(raft_river_use$Patch_ID==raft_river_levs[i]),]
  
  m0_RR<-stan_glmer(raft_river_bound~1+(1|Patch_ID),data=raft_river_in[[i]],cores=4, family = "binomial", iter=10000)
  
  # Making predictions for the left out data
  null_preds[[i]]=posterior_epred(m0_RR,newdata=raft_river_out[[i]])
  
  mPRED_RR<-stan_glmer(raft_river_bound~CP_Pred_std+Phenolics_Pred_std+Monoterpenes_Pred_std+(1|Patch_ID),data=raft_river_in[[i]],cores=4, family = "binomial", iter=10000)
  
  pred_preds[[i]]=posterior_epred(mPRED_RR,newdata=raft_river_out[[i]])
  
  mREF_RR<-stan_glmer(raft_river_bound~CP_Ref_std+Phenolics_Ref_std+Monoterpenes_Ref_std+(1|Patch_ID),data=raft_river_in[[i]],cores=4, family = "binomial", iter=10000)
  
  ref_preds[[i]]<-posterior_epred(mREF_RR,newdata=raft_river_out[[i]])
  }

null_preds_t<-t(null_preds)

# Extracting the predictions
# Binding the results together in a single data frame
raft_river_logo<-vector("list",4)
names(raft_river_logo)<-c("out_data","null","ref","pred")
raft_river_logo[[1]]<-do.call("rbind",raft_river_out)
raft_river_logo[[2]]<-t(do.call("cbind",null_preds))
raft_river_logo[[3]]<-t(do.call("cbind",ref_preds))
raft_river_logo[[4]]<-t(do.call("cbind",pred_preds))

# Save the object 
save(raft_river_logo,file="raft_river_logo.Rdata")

# Load(file="raft_river_logo.Rdata")
str(raft_river_logo)

# Predicted data
# These are the predictions from the three models above. These are matrices, because we are doing this in a Bayesian context. 
null_preds=raft_river_logo$null
ref_preds=raft_river_logo$ref
pred_preds=raft_river_logo$pred

# New variable
raft_river_obs<-raft_river_logo$out_data$raft_river_bound[,1]

# New variable

raft_river_total <- raft_river_logo$out_data$raft_river_bound[,2]

raft_river_null<-apply(null_preds,1,mean)
length(raft_river_null)
raft_river_ref<-apply(ref_preds,1,mean)
length(raft_river_ref)
raft_river_pred<-apply(pred_preds,1,mean)
length(raft_river_pred)

# Likelihood of observed data, given predicted data. 

-sum(dbinom(raft_river_obs,prob=raft_river_ref/raft_river_total,size=50,log=T),na.rm=T)
-sum(dbinom(raft_river_obs,prob=raft_river_null/raft_river_total,size=50,log=T),na.rm=T)
-sum(dbinom(raft_river_obs,prob=raft_river_pred/raft_river_total,size=50,log=T),na.rm=T)

# Mean absolute error, defined above. This is on the scale of the data, so the negative log likelihoods (which are a bit abstract) make more sense. 
mae(raft_river_null,raft_river_obs) 
mae(raft_river_ref,raft_river_obs)
mae(raft_river_pred, raft_river_obs)
```

# General posterior draw descriptive statistics

```{r}

nameo <- list.files()[-1]

chem_range <- read.csv("Chemistry_Mins_Max.csv")

load("mREF_RR_single.Rdata")
load("mPRED_RR_single.Rdata")

#All chemicals
chemm <- read.csv("Text_Chemistry_Mins_Max_13July2023.csv")

#First we will pull out the posterior draws:
ref_RR_posteriors <- data.frame(mREF_RR_single)
pred_RR_posteriors <- data.frame(mPRED_RR_single)

dim(ref_RR_posteriors)
dim(pred_RR_posteriors)

```

# Probability of Direction - Reference Chemistry

What is the percentage of draws that are either positive of negative?

```{r}

# Crude Proteins
length(which(ref_RR_posteriors$CP_Ref_std>0))/length(ref_RR_posteriors$CP_Ref_std)
length(which(ref_RR_posteriors$CP_Ref_std<0))/length(ref_RR_posteriors$CP_Ref_std)

# Monoterpenes
length(which(ref_RR_posteriors$Monoterpenes_Ref_std>0))/length(ref_RR_posteriors$Monoterpenes_Ref_std)
length(which(ref_RR_posteriors$Monoterpenes_Ref_std<0))/length(ref_RR_posteriors$Monoterpenes_Ref_std)

# Phenolics
length(which(ref_RR_posteriors$Phenolics_Ref_std>0))/length(ref_RR_posteriors$Phenolics_Ref_std)
length(which(ref_RR_posteriors$Phenolics_Ref_std<0))/length(ref_RR_posteriors$Phenolics_Ref_std)

```

# Probability of Direction - Predicted Chemistry

What is the percentage of draws that are either positive of negative?

```{r}

# Crude Proteins
length(which(pred_RR_posteriors$CP_Pred_std>0))/length(pred_RR_posteriors$CP_Pred_std)
length(which(pred_RR_posteriors$CP_Pred_std<0))/length(pred_RR_posteriors$CP_Pred_std)

# Monoterpenes
length(which(pred_RR_posteriors$Monoterpenes_Pred_std>0))/length(pred_RR_posteriors$Monoterpenes_Pred_std)
length(which(pred_RR_posteriors$Monoterpenes_Pred_std<0))/length(pred_RR_posteriors$Monoterpenes_Pred_std)

# Phenolics
length(which(pred_RR_posteriors$Phenolics_Pred_std>0))/length(pred_RR_posteriors$Phenolics_Pred_std)
length(which(pred_RR_posteriors$Phenolics_Pred_std<0))/length(pred_RR_posteriors$Phenolics_Pred_std)

```

# Effect Size Min & Max

```{r}

# Referencing min and max from data frame
chemm$Ref_Min[which(chemm$Site=="RR" & chemm$Chemical=="Crude Protein")] 
chemm$Ref_Max[which(chemm$Site=="RR" & chemm$Chemical=="Crude Protein")] 

# Setting up an empty vector to fill in with predictions
predicted_diff_cp_ref <- rep(NA,times=ncol(ref_RR_posteriors))
predicted_diff_Monoterpenes_ref <- rep(NA,times=ncol(ref_RR_posteriors))
predicted_diff_Phenolics_ref <- rep(NA,times=ncol(ref_RR_posteriors))

# CP

for(i in 1:ncol(ref_RR_posteriors)){

# This is just an intercept + slope*x. plogis ensures it is a probability. We are looping over every value of the posterior draw to propagate uncertainty.
min_pred<-plogis(ref_RR_posteriors$X.Intercept.[i]+ref_RR_posteriors$CP_Ref_std[i]*chemm$Ref_Min[which(chemm$Site=="RR" & chemm$Chemical=="Crude Protein")])
  
max_pred<-plogis(ref_RR_posteriors$X.Intercept.[i]+ref_RR_posteriors$CP_Ref_std[i]*chemm$Ref_Max[which(chemm$Site=="RR" & chemm$Chemical=="Crude Protein")])
  
predicted_diff_cp_ref[i]<-max_pred-min_pred # This is the difference we will store. 
  }  

quantile(predicted_diff_cp_ref,c(0.025,0.5,0.975))

# Monoterpenes
for(i in 1:ncol(ref_RR_posteriors)){

# This is just an intercept + slope*x. plogis ensures it is a probability. We are looping over every value of the posterior draw to propagate uncertainty.
min_pred<-plogis(ref_RR_posteriors$X.Intercept.[i]+ref_RR_posteriors$Monoterpenes_Ref_std[i]*chemm$Ref_Min[which(chemm$Site=="RR" & chemm$Chemical=="Monoterpenes")])
  
max_pred<-plogis(ref_RR_posteriors$X.Intercept.[i]+ref_RR_posteriors$Monoterpenes_Ref_std[i]*chemm$Ref_Max[which(chemm$Site=="RR" & chemm$Chemical=="Monoterpenes")])
  
predicted_diff_Monoterpenes_ref[i]<-max_pred-min_pred # This is the difference we will store. 
}  

quantile(predicted_diff_Monoterpenes_ref,c(0.025,0.5,0.975))


# Phenolics
for(i in 1:ncol(ref_RR_posteriors)){

# This is just an intercept + slope*x. plogis ensures it is a probability. We are looping over every value of the posterior draw to propagate uncertainty.
min_pred<-plogis(ref_RR_posteriors$X.Intercept.[i]+ref_RR_posteriors$Phenolics_Ref_std[i]*chemm$Ref_Min[which(chemm$Site=="RR" & chemm$Chemical=="Phenolics")])
  
max_pred<-plogis(ref_RR_posteriors$X.Intercept.[i]+ref_RR_posteriors$Phenolics_Ref_std[i]*chemm$Ref_Max[which(chemm$Site=="RR" & chemm$Chemical=="Phenolics")])
  
predicted_diff_Phenolics_ref[i]<-max_pred-min_pred # This is the difference we will store. 
}  

quantile(predicted_diff_Phenolics_ref,c(0.025,0.5,0.975)) 

```

# Effect Size Min & Max - Predicted Chemistry

```{r}

# Referencing min and max from data frame
chemm$Pred_Min[which(chemm$Site=="RR" & chemm$Chemical=="Crude Protein")] 
chemm$Pred_Max[which(chemm$Site=="RR" & chemm$Chemical=="Crude Protein")] 

# Setting up an empty vector to fill in with predictions
predicted_diff_cp_pred <- rep(NA,times=ncol(pred_RR_posteriors))
predicted_diff_Monoterpenes_pred <- rep(NA,times=ncol(pred_RR_posteriors))
predicted_diff_Phenolics_pred <- rep(NA,times=ncol(pred_RR_posteriors))

# CP
for(i in 1:ncol(pred_RR_posteriors)){

# This is just an intercept + slope*x. plogis ensures it is a probability. We are looping over every value of the posterior draw to propagate uncertainty.
min_pred<-plogis(pred_RR_posteriors$X.Intercept.[i]+pred_RR_posteriors$CP_Pred_std[i]*chemm$Pred_Min[which(chemm$Site=="RR" & chemm$Chemical=="Crude Protein")])
  
max_pred<-plogis(pred_RR_posteriors$X.Intercept.[i]+pred_RR_posteriors$CP_Pred_std[i]*chemm$Pred_Max[which(chemm$Site=="RR" & chemm$Chemical=="Crude Protein")])
  
predicted_diff_cp_pred[i]<-max_pred-min_pred # This is the difference we will store. 
  }  

quantile(predicted_diff_cp_pred,c(0.025,0.5,0.975))


# Monoterpenes
for(i in 1:ncol(pred_RR_posteriors)){

# This is just an intercept + slope*x. plogis ensures it is a probability. We are looping over every value of the posterior draw to propagate uncertainty.
min_pred<-plogis(pred_RR_posteriors$X.Intercept.[i]+pred_RR_posteriors$Monoterpenes_Pred_std[i]*chemm$Pred_Min[which(chemm$Site=="RR" & chemm$Chemical=="Monoterpenes")])
  
max_pred<-plogis(pred_RR_posteriors$X.Intercept.[i]+pred_RR_posteriors$Monoterpenes_Pred_std[i]*chemm$Pred_Max[which(chemm$Site=="RR" & chemm$Chemical=="Monoterpenes")])
  
predicted_diff_Monoterpenes_pred[i]<-max_pred-min_pred # This is the difference we will store. 
}  

quantile(predicted_diff_Monoterpenes_pred,c(0.025,0.5,0.975)) 

# Phenolics
for(i in 1:ncol(pred_RR_posteriors)){

# This is just an intercept + slope*x. plogis ensures it is a probability. We are looping over every value of the posterior draw to propagate uncertainty.
min_pred<-plogis(pred_RR_posteriors$X.Intercept.[i]+pred_RR_posteriors$Phenolics_Pred_std[i]*chemm$Pred_Min[which(chemm$Site=="RR" & chemm$Chemical=="Phenolics")])
  
max_pred<-plogis(pred_RR_posteriors$X.Intercept.[i]+pred_RR_posteriors$Phenolics_Pred_std[i]*chemm$Pred_Max[which(chemm$Site=="RR" & chemm$Chemical=="Phenolics")])
  
predicted_diff_Phenolics_pred[i]<-max_pred-min_pred # This is the difference we will store. 
}  

quantile(predicted_diff_Phenolics_pred,c(0.025,0.5,0.975)) 

```

